\documentclass[12pt]{article}

\input{\string~"/Insync/templates/preamble2"}

\title{Framing}

\date{\today}

\begin{document}

\maketitle

%\section*{\st{Prospectus Revisions}}
%	\begin{coi}
%		\item \st{Ryan: Replace focus group with online MTurk. That can give me the same insights for a lot less money and effort}
%		\item \st{Proofread everything}
%	\end{coi}

%\section*{Pre-Polls}
%	\begin{coi}
%		\item I need to know how many pre-polls I'm running and how much money I should allocate for that (since it all needs to be within the Provost money)
%		\item I need to know that now because I need to tell Lucid how much much I'm paying them by mid-March
%		\item The current setup from the proposal is meta-analysis, three simple polls, experiment:
%			\begin{coi}
%				\item The meta-analysis gives me a list of all statistically significant frames
%				\item Poll \#1 asks respondents to rate how moral each argument in each of those frames is
%				\item Poll \#2 asks people what they consider moral arguments to be. I use the insights from poll \#2 to design frames for each of the `missing' frames in previous experiments (the idea being that no experiment so far has tested for positive/negative moral/amoral frames and there thus will be gaps)
%				\item Poll \#3 tests how moral/amoral my designed frames are
%				\item Then finally comes the survey experiment
%			\end{coi}
%		\item I have \$4,830. If I did one simple one for \$0.10 at 200 respondents, that would cost me \$28. So it would be \$84 for three simple polls with 200 respondents each, which leaves me with \$4,746. My R method online with Lucid costs \$2 each, so that would make 2,373 respondents for the experiment. That would leave 474 respondents per treatment group
%		\item Money-wise, that would work out. Now I need to know whether the proposal setup (meta-analysis, pre-polls) is feasible to do in a realistic time frame, with me teaching in both terms
%		\item Very good point from Ryan: He totally sees the point of polls 1 and 3, but not really poll 2. Removing 2 would obviously change the financial numbers -- but Rune Slothuus for instance said my idea for the open-ended poll about what makes frames moral is good
%		\item Jeff and Matt agree: Ditch poll \#2
%		\item Go with 300 respondents for each of the remaining pre-polls. To make sure people pay more attention to the frames, pay \$0.20 each. That comes out to \$168 for both pre-polls, which leaves \$4,662 for Lucid, which gives me 2,331 respondents, which means 466 respondents per treatment group
%	\end{coi}

\section*{General}
	\begin{coi}
		\item Design moral and unmoral frames and pretest both on MTurk, then use the `proven' frames for the survey experiment. This is a chapter on framing where I apply both methods in the experiment, analyze the methods' performances, and analyze the substantive results in terms of moral frames (the latter is where I produce/add some nuance in our understanding of framing)
		\item Using the experiment as the application for both papers
			\begin{coi}
				\item Paper I: One half of the sample gets the ordinal probit education categories, the other gets the original ones without giving respondents \texttt{Don't Know/Refuse} options. Compare the differences between the ordered probit and the original results whilst knowing which one is closer to the truth based on the simulation results
				\item Paper II: Use the resulting completely observed data, introduce random missing data, and show how the ordinal affinity score method performs on ordinal variables compared with other method	. Assess the performance of the ordinal affinity score method because we know the true values of the completely observed data
			\end{coi}
	\end{coi}	
		

\section*{Order}
	\begin{coi}
		\item Rework theory, design frames/questionnaire
		\item Pre-test
		\item New IRB approval
		\item Pre-analysis plan and pre-registration
		\item Field experiment
		\item Analysis of the results
	\end{coi}


\section*{Rework theory, design frames/questionnaire}
	\begin{coi}
		\item I have sent Liz an email with my current framing chapter and the questionnaire from the previous experiment. I recall that she had various input on the chapter setup, the experiment design, and the questionnaire, so I thought it best to start out from these documents. She emailed back with general instructions to sharpen up the theoretical part. I then researched the literature, and we had a Zoom call on June 23. The main change from that talk is that I will juxtapose moral frames (i.e. values) with self-interest frames. This is more precise and clear-cut than the vague `amoral' frame category that we can't be sure even exists
		\item After researching and reading a lot, I emailed Liz again with the following design idea. She signed off on it. It's not a major change. I basically only adds a moderator as a further nuance:
			\begin{coi}
				\item Moral conviction literature tells us that people with moralized attitudes hold those attitudes strongly. I take from this that these people's attitudes can't be moved, no matter what opposing or supporting moral or self-interest frames we give them. We can only move the attitudes of people who don't hold highly moralized attitudes, since there is room for movement here
				\item I thus suggest to separate respondents into those who hold moralized attitudes on an issue and those who don't. To do so, I would first give all respondents descriptions of what `moral' is and what `self-interest' is, for instance: ``Moral concerns what people should or should not do etc." and ``Self-interest concerns actions and attitudes that only suit yourself etc." (obviously I need to flesh these out much more). I will take the `moral' description directly from Ryan. He essentially took Skitka's moral conviction measure (below) and added the `moral' description. I will take that and further add the `self-interest' description
				\item I would then use Tim Ryan's version of Skitka's moral conviction measure (asking respondents ``To what extent is your position on [issue] a reflection of your core moral beliefs and convictions" and ``... connected to your fundamental beliefs about right and wrong?") -- with the tweak that I don't ask them about their position on the issue, but about their attitude towards the issue overall. Let's say that the issue is abortion. I give respondents the descriptions of `moral' and `self-interest'. I then ask them: ``To what extent is your position on abortion a reflection of your core moral beliefs and convictions" and ``To what extent is your position on abortion connected to your fundamental beliefs about right and wrong?" -- but without actually asking them about their position yet (basically leaving that open until they get the frame). The alternative is that I ask them about their position on abortion twice. I would here (1) ask them where they stand on abortion on 1-5 Likert, (2) give them the descriptions, (3) measure moral conviction, (4) randomly assign a frame, (5) ask them where they stand on abortion on 1-5 Likert again. The big problem with that is anchoring. Liz agrees with my approach. While it's better to have people write down their stands (more concrete for them and also allows me to be more precise in my analyses), the downside effect of anchoring is a pretty big (too big) downside
				\item After I measure moral conviction on their attitude towards the issue (1-5 Likert; ``Not at all", ``Slightly", ``Moderately", ``Much", ``Very much"), every respondent randomly gets one of the five frames: opposing moral frame, opposing self-interest frame, control frame, supporting moral frame, supporting self-interest frame. Every respondent then registers his support/opposition to the issue on another 1-5 Likert scale (``Strongly oppose" ... ``Strongly approve")
				\item For the respondents with highly moralized attitudes on the issue, their support/opposition for the issue should be statistically the same across all frames -- since their attitudes are set and can't easily be moved. For the respondents without highly moralized attitudes on the issue, the frames should move responses towards support or opposition, depending on the direction of the frame. For these people, we can see whether the moral or the self-interest frames cause bigger shifts. I would expect moral frames to cause bigger shifts for highly moralized, since moral arguments likely fall on fertile ground here. For low moralized, I would expect self-interest frames to cause bigger shifts, since these people reject the importance of morals for the issue
				\item Insights that I can see:
					\begin{coi}
						\item We can test which issues are considered more moral than others 
						\item We can test whether people with highly moralized attitudes really stick to their pre-formed attitudes, no matter what they're exposed to 
						\item We can test whether people with low moralization are more influenced by moral or self-interest frames 
						\item We can test whether people with no moralization are most influenced by arguments based on self-interest 
					\end{coi}
			\end{coi}
		\item Reorganize chapter outline
		\item Expand framing section
			\begin{coi}
				\item Outline differences between equivalency and emphasis frames (I'm looking at emphasis)
				\item Outline differences between emphasis frames and new information (Leeper \& Slothuus)
				\item Clearly express that we do know why frames work (Zaller: Frames move persuasive information to the top of one's mind) but that we don't know why some frames are successful at moving persuasive information to the top of one's mind and others aren't. This was not initially clear to Liz
			\end{coi}
		\item Set up section on morality from the literature
			\begin{coi}
				\item Incorporate Stoker on public opinion in the public sphere (i.e. her stuff on ethics)
				\item Is there theorizing on ``value frames" or ``moral frames" (Stoker, Google Scholar)?
				\item Jamie's article he sent me
				\item Chris Wolsko
				\item Willer and Feinberg (how they used MFT)
				\item I need a description of `morality`. I can take that from Tim Ryan
				\item I need criteria along which I can construct the frames. For morals or values, Moral Foundations Theory is an option. Liz has also written about this in her diss. I'm not sure whether to go with MFT, since it's so party-ID based, though
				\item Feldman chapter in the Oxford Handbook of Political Psychology (some time around 2016 or so) -- gives a more complete overview of the field
				\item Kinder on the ``primary ingredients" of public opinion (one of which is ``matters of principle"), Feldman on values, Milton Rokeach on values
			\end{coi}
		\item Set up section self-interest from the literature
			\begin{coi}
				\item Look at the paper I wrote for Liz' class for works on self-interest
				\item I need a description of `self-interest'
				\item I need criteria along which I can construct the frames
			\end{coi}
		\item Choose issues based on the literature and what works for perceived self-interest
		\item Design issue frames built on morals and self-interest
			\begin{coi}
				\item Do I use stuff from MFQ?
			\end{coi}
		\item Connect everything up coherently
		\item Send it to everyone for feedback
		\item Email Lucid to arrange experiment to be run before the end of the year
		\item Morals
			\begin{coi}
				\item Leave out moral conviction, it just complicates things because conviction and MFT don't play well together $\rightarrow$ DONE
				\item Play down the language on Haidt a bit. He exaggerates the differences between parties. There is nothing sacred about pid in Haidt, the values are what matters. He just shows that Dems and Reps differ on average with respect to the foundations, i.e. not all Dems have the Dem pattern and vice versa $\rightarrow$ DONE
				\item As I talk about moral vs. nonmoral issues, make sure to mention that I'm about moral and self-interest frames, not the issues. Don't get lost in the issue discussion, so that readers won't think I'm mainly about the issues $\rightarrow$ DONE
				\item Fix disjuncture between theory and design: I say that moral frames work because people have emotional attachments to their morals/values/whatever, but then I posit that moral frames work among people without moral conviction. Why would morals influence people who don't seem to have morals? $\rightarrow$ DONE
				\item Forget about pid, just ask people about their moral preferences, the same way I ask about their self-interest tax burdens (directionality, where you stand). Measure self-interest, measure moral foundations for each respondent (i.e. query where they stand on the particular moral foundation) -- use parts of MFQ $\rightarrow$ DONE
				\item Find moral frames that appeal to all (or most) people. Fasten on some moral foundations that I think map best to each of the two issues $\rightarrow$ DONE
			\end{coi}
		\item Self-interest
			\begin{coi}
				\item Kinder is one of the doubters that self-interest matters all that much. Make sure I only cite him that way $\rightarrow$ DONE
				\item Do Campbell, Converse, Miller, and Stokes really say self-interest is the main driver of political opinion? -- They don't. Delete that reference $\rightarrow$ DONE
				\item Political psychologists who talk about self-interest are definitely not rational choices. Don't put everyone on this topic into the rat choice rat hole. Self-interest is not automatically part of rat choice $\rightarrow$ DONE
				\item Move away from material self-interest. Material self-interest is not the same thing as self-interest. Don't limit my study to that, since I'm biasing my findings against self-interest right out of the gate. This narrow understanding of self-interest is precisely why researchers have found little evidence of it in public opinion $\rightarrow$ DONE
				\item Leave out perceived self-interest (i.e. not make it a major thing) $\rightarrow$ DONE
				\item Define self-interest as related to personal autonomy, health/safety, wealth, and status (Weeden and Kurzban, evolutionary psychology). No need to include family well-being (that's too far for my purposes). Example of ``non-material" but obvious self-interest: Young guys who oppose hawkish Presidents because they don't want to be drafted are acting in their self-interest. Women of child bearing age who want to be free from the possibility of an unwanted pregnancy may support abortion rights out of self-interest $\rightarrow$ DONE
				\item Set up competing self-interests that people have (e.g. everyone wants low taxes, everybody wants to be healthy) $\rightarrow$ DONE
			\end{coi}
		\item Frames
			\begin{coi}
				\item Move away from the whole ``move to the top of people's minds" thing. That's priming, not framing, and it doesn't fit my theoretical setup. I'm doing strong and weak frames, particularly whether moral or self-interest frames are more likely to compel people to change a specific attitude. The term ``frame" comes from the idea of framing a picture. If you were to photograph a scene, you might choose to include some details and exclude others and, when you do so, that changes the way people will interpret the scene $\rightarrow$ DONE
				\item Move away from ``more important in shaping political attitudes". My chapter focuses on ``what makes a strong frame", with the assertion that ``strong frames are moral frames". A chapter focusing on ``what is more important in people's attitude formation, morals or self-interest?" is too general of a question and also has been looked at by others. Make sure it's specifically about the juxtaposition of moral vs. self-interest in frames, not in general $\rightarrow$ DONE
				\item Engage more with Druckman and Chong (2007) since they differentiate weak from strong frames $\rightarrow$ Druckman and Chong (APSR, 2007) ask respondents in a pre-test what arguments they consider strong or weak for the issues they chose. Druckman and Chong then assert that frames containing arguments deemed strong are strong frames and frames containing arguments deemed weak are weak frames. They then use these strong and weak frames in their actual experiment. They let people decide pre-experiment what they consider strong, which doesn't give any insights as to what actually makes a frame strong. We just know which are considered strong and weak, but not why $\rightarrow$ DONE
				\item 5 frames per issue $\rightarrow$ DONE
				\item Find one other issue. Ditch taxes for ... national security, infrastructure (something where self-interest and moral frames are each roughly equally strong). For healthcare: Healthcare costs and health insurance costs  may be very different things (p. 83). I may love paying \$0 for insurance, but hate that my out-of-pocket expenses are enormous. Make sure I consistently stick to one and don't mix them up $\rightarrow$ DONE
				\item My frames are not actually frames, since I'm describing different policies. To build stimuli appropriate for testing my theory, I need to keep the content (scene) the same across the various treatment groups but change what implications are emphasized, e.g. a low cost health care plan might save tax payer money or harm poor people. Set up a policy with some meat on it, something more substantial that is the same across treatment groups $\rightarrow$ DONE
				\item Make frames a bit longer in terms of sentences. Have them read articles, bigger things, longer, more, not just one sentence $\rightarrow$ DONE
			\end{coi}
		\item Miscellaneous
			\begin{coi}
				\item Palin example needs to go -- that's providing new (mis)information, not a frame $\rightarrow$ DONE
				\item Cite literature to back up content in the introduction $\rightarrow$ DONE
				\item I say in the introduction that morals have supplanted self-interest over time and recently. It sounds like I'm asserting that, when I'm actually just referring to what scholars are saying. Be more explicit and back it up, e.g.: Scholars suggest that morals have supplanted self-interest over time. Frank (2004), Haidt (2012) and several others argue that morals are more important now $\rightarrow$ DONE
			\end{coi}
		\item Send chapter to Liz
		\item Questionnaire
			\begin{coi}
				\item Healthcare $\rightarrow$ DONE
					\begin{coi}
						\item Single-payer, tax-based, universal, pay healthcare by taxes, government hired the companies -- too direct, too detailed, take that out. ``Improving healthcare in the US", ``paid through a mix of individual and employer fees", keep everything much more vague, not many details so as not to put anyone off
						\item Moral supporting: ``Affordable healthcare for everyone" -- that's self-interest. Find some form of ``this doesn't help/hurt you, but it will help poor/elderly people"
						\item Moral opposing: Vulnerable/Elderly people will get substandard care, long lines, no appointments etc.
						\item Self-interest supporting is good
						\item Self-interest opposing: The typical person needs to pay more (move away from the autonomy of decisions here)
					\end{coi}
				\item Environment $\rightarrow$ DONE
					\begin{coi}
						\item Don't use climate change, stay with some kind of environmental restrictions/regulations, e.g. preventing companies from dumping chemicals into the water, something like that. But phrase it as generally as possible so as not to trigger anyone
						\item Moral supporting restrictions: Poor people are harmed by companies without regulations
						\item Moral opposing restrictions: Difficult for people to comply with regulations, poor people might lose their job when companies need to pay more. The people who deforest need money from logging, with restrictions they don't have any income any more. Same for fisheries
						\item Self-interest supporting restrictions: Otherwise we might get cancer and die
						\item Self-interest opposing restrictions: Restrictions costs money, you will pay more for products
					\end{coi}
				\item ``How much does Care/Harm and how much does self-interest matter to you?" -- I do that very well with the MFQ questions. Now I need to get a self-interest scale comparable to the MFQs that estimates, overall, how selfish (i.e. self-interested) a person is (WITHOUT asking about each issue, just asking in general) $\rightarrow$ DONE
				\item shiny
					\begin{coi}
						\item Remove the last question about the code as it may deter people from completing since Lucid gives everyone an RID value when they complete $\rightarrow$ DONE
						\item Do multiple attention checks in different formats (apparently important for Lucid). From Ryan: \href{https://www.qualtrics.com/blog/using-attention-checks-in-your-surveys-may-harm-data-quality/}{Qualtrics}, \href{https://onlinelibrary.wiley.com/doi/10.1111/ajps.12396}{Wiley} $\rightarrow$ DONE
						\item Set up that each respondent randomly sees (and gets blocked on) either ordered probit or ANES $\rightarrow$ DONE
						\item After speaking with Jeff and Ryan, here is the final setup: I split the sample into ANES and probit categories. Each respondent randomly gets one or the other. I save the assigned data for each set in separate folders. Probit respondents are in /seqblock.op, ANES respondents are in /seqblock.an. So I get two datasets per issue. I assign treatment for the issues independently, i.e. respondents are not assigned to the same treatment group for both issues. I speed things up a bit by incorporating observeEvent() into eventReactive() when treatment is assigned. That eliminates the additional download I had before. I block only on education (so I took pid out)
					\end{coi}
				\item \hl{Safe-guarding against file-write traffic jam}
					\begin{coi}
						\item I have tested it simultaneously on two laptops. When one laptop is accessing Dropox, the other simply waits, then accesses Dropbox itself. There is no error or other conflict. That means if 50 people click it at the same time, the 50th person would have a 1-minute lag. It's not ideal but not a big problem
						\item Add one sentence in brackets to the assignment pages that it might take a bit for the code too load, that they please not quite the browser etc.
					\end{coi}				
			\end{coi}
		\item \hl{Power analysis}
			\begin{coi}
				\item Do a power analysis to be sure that I have a chance to detect typical framing effects. There is an R function for that, use that (\texttt{declareDesign}?). Also 	email Jeff a reminder that he sends me slides for the sample size calculation
			\end{coi}
		\item \hl{Crispify writing}
			\begin{coi}
				\item Top of p. 80:  See Jim Gibson, and others, add stuff on procedures vs outcomes
				\item 4.2, middle of p. 82: See Brooks and Manza here on public opinion and welfare state support (since I'll use healthcare, especially)
				\item Expand discussion of the limitations and problems with using MTurk for social research a bit, use \begin{verbatim} @huff_who_2015; @clifford_2015_samples; @stritch_2017_opportunities; @burnham_2018_mturk \end{verbatim} (all already downloaded)
				\item Expand discussion of limitations and problems with using Lucid for social research a bit as well, use \begin{verbatim} @coppock_2019_validating \end{verbatim}
				\item Add a few lines that I added a factual manipulation check (treatment-independent), \begin{verbatim} @kane_2019_harm \end{verbatim}
				\item First paragraph p. 74: Use Rokeach (his book from the 1960s) for a more intuitive description of what it means to be moral, i.e. values as ``oughts" and ``shoulds". Either switch Skitka's (1), (2), (3) for Rokeach or say that Skitka says that people FEEL it's an objective truth (not that she's actually stating that morals are objective truths)
				\item Second paragraph p. 74: This part meanders around, goes back and forth between issues and arguments/frames. Restructure it, make my point more clearly, it's a bit muddied and hard to follow now
				\item There is a short article by Haidt that provides numerical means for liberals and conservatives. Include those numbers where I talk about the foundations. Don't use numbers for each foundation, use averages for all the conservative ones and the liberal ones. We want to have some idea of the effect sizes for the ideological differences for the foundations, something we can measure. Also add some more language that the distinctions Haidt makes are all tendencies, not more
				\item Weeden and Kurzban: Dial it back a little, be less of a fan boy. I went too much to the other side. Present the other side more, the one I had too much of before (the one where self-interest is financial). Present both sides, then say which side I fall on. Also avoid first person when I talk about the side I fall on
				\item Include argument why I choose environment as my second issue
				\item Include the origins of the self-interest measurement questions (and some general citations for this)
			\end{coi}
	\end{coi}
	

\section*{Apply for new IRB approval $\rightarrow$ DONE}

\vspace{0.4cm}

\section*{Set up pre-registration on OSF (from RT2 training)}
	\begin{coi}
		\item Created account
		\item \hl{Slowly fill in the details as I go along}
		\item If I want to mention that in the paper, I can quote articles in the BITSS /readings folder
		\item Note: Just because you have a pre-analysis plan doesn't mean that's all you can do with your data (and it doesn't mean exploratory analysis is now forbidden). If there is a good theoretical motivation that you can defend, then you can do that
	\end{coi}

\section*{Pre-test}
	\begin{coi}
		\item To test designed frames
		\item \hl{Set pre-test up according to Liz' emails}
		\item 600 respondents, \$0.20 each (or 400 at \$0.40 each)
	\end{coi}

\section*{Field experiment}
	\begin{coi}
		\item \hl{Lucid attention checks}
			\begin{coi}
				\item Can Lucid weed out people who fail my attention checks so I don't have to pay for people who fail it? $\rightarrow$ asked them
			\end{coi}
		\item \hl{Code checks}
			\begin{coi}
				\item (Be INCREDIBLY careful with any randomization of response options. Many things in the code use the corresponding number for respondents' response selections, not the actual words, so messing with the order is a very delicate thing)
				\item Are the education categories blocked like I want?
				\item Are all the responses being saved to Dropbox like I want?
				\item Do all the treatment group .txt files contain the correct corresponding frames?
				\item Are the correct .txt files shown in the survey depending on the group I'm being blocked into?
				\item Are the apostrophes working?
				\item Are the words ``environment" and ``healthcare" in each frame setup (for the checks)?
			\end{coi}
		\item Final tasks
			\begin{coi}
				\item Do 200 trials, then see that everything was blocked properly for both sets of education categories (i.e. check that in R and on Dropbox)
				\item Delete everything in all /alldata and /seqblock folders
				\item Re-deploy app
			\end{coi}
	\end{coi}
	
\section*{Analysis of the results}
	\begin{coi}
		\item Most straightforward is to use the method I use to block
		\item But I also have lots of good resources how to analyze ordinal variables as EVs, instead of turning them into intervals for a normal regression, including a Bayesian way
		\item Apply blocking and missing data to the data, i.e. do a blocking and missing data analysis on the framing data (since the framing data is no longer part of the blocking and missing data chapters)
	\end{coi}














\end{document}
