\input{/Users/simonheuberger/Dropbox/work/latex/preamble}

\title{Money}

\date{\today}

\begin{document}

\maketitle



\section*{General}
	\begin{coi}
		\item All reimbursement requests for the Provost scholarship must be RECEIVED by Anita Brown (\href{mailto:abrown@american.edu}{abrown@american.edu}) by April 11, 2019. Anything received after that won't be reimbursed
		\item Find out what I will use the money for. If I use MTurk, no problem, just upload it. If I use it for something else, time is short. Using an MTurk sample and an undergrad sample makes no sense. They're not comparable on so many levels, and that's useless for a mode difference comparison
		\item One MTurk online sample, one MTurk sample that gets phoned
			\begin{coi}
				\item It's definitely possible to do phone interviews on MTurk, \href{https://customerdevlabs.com/2012/08/21/using-mturk-to-interview-100-customers-in-4-hours/}{see here}
				\item Ryan suggested that, if I go with MTurk, I should consider making the HIT so that someone has to be willing to be contacted both by phone or not.  Then I could randomly select from that group into the two modes.  That might be useful to have comparability across modes
				\item Natalie said MTurk is a decent fallback if other stuff doesn't work out
			\end{coi}
		\item One undergrad sample online, one undergrad sample face-to-face. I don't need a physical setting to interview people -- I `just' need help with recruiting participants. Then one half gets it via email, the other I interview one at a time
			\begin{coi}
				\item Kogod Econ Behavioral Lab
					\begin{coi}
						\item Not gonna work
						\item They can only help with studies that are run in their lab, not with online or phone stuff. The person I'm emailing with mentioned that she once recruited people through Today@AU -- that's no longer active. The other stuff she suggested is pointless -- putting up ads around campus, snowballing system ... 
					\end{coi}
				\item Psych department
					\begin{coi}
						\item Not gonna work
						\item The woman there just told me to get a list with students' contacts from my department ...
					\end{coi} 
			\end{coi}
		\item Subsample of the TAPS participants, then half gets it online and half by phone (suggested by Jeff, contacted Michelle)
			\begin{coi}
				\item Not gonna work
				\item TAPS is no longer active and very confidential with participant contacts. It also used to provide participants with devices and internet access for the online sample -- which they don't do any more.
			\end{coi}
		\item Lucid (suggested by Michelle, Jonathan, Natalie (through Jeff))
			\begin{coi}
				\item Jonathan and Michelle both heard really good things
				\item Natalie also said it's a good option
				\item I wrote to them and told them what I would need (two modes, two assignment methods, \$5k spent by April)
				\item Someone from Lucid called me and we spoke for half an hour. She then sent me a summary of our call via email (subject: ``Survey Experiment for American U with Lucid"). I think it has potential
				\item I emailed a situation update with Lucid's services and prices to Matt, Ryan, and Jeff
				\item They all voiced the same concern: What if I pay for those phone numbers and then no one picks up?
				\item I emailed extensively with Lucid about that. Long story short: They don't have a plan that offers payment for completed phone responses. Worse yet: Lucid told to expect a 90 \% nonresponse rate, based on experiences some clients of theirs had with similar studies. That would mean paying for 200 numbers but only getting 20 responses. That's moronic and no good
				\item Tell Lucid it won't work with the phone stuff, but I might very well come back to them with the online stuff, depending on what I decide with my committee
			\end{coi}
		\item Qualtrics, SSI, NORC (suggested by Natalie (through Jeff))
			\begin{coi}
				\item Natalie has contacts at all three and said she would put me in touch with them
				\item Qualtrics: Skeptical whether they do phone
				\item SSI/ResearchNow/Dynata: Definitely do phone and online, but not sure how far \$5k would go
				\item NORC: High quality, definitely do phone and online, very likely to be way too expensive
				\item Emailed Natalie and asked her to put me in touch with Qualtrics, SSI, NORC, but it's very likely pointless anyway
			\end{coi}
		\item Situation so far: Undergrads are out. TAPS is dead. Lucid phone stuff is moronic. Qualtrics very likely won't have phone. My money very likely won't get me much with SSI and NORC. I'll keep trying with Qualtrics, SSI, NORC through Natalie, but I also want to put a failsafe strategy in place. That includes everything from simply going with MTurk to scrapping/changing the modes paper (since that is the hard part), in which case I could use my money for the Lucid online stuff. I emailed Jeff, Matt, Ryan about all of this
			\begin{coi}
				\item Ryan
					\begin{coi}
						\item Look for other options to have as paper II, instead of the phone mode comparison
						\item Have MTurk as the fallback option
					\end{coi}
				\item Matt
					\begin{coi}
						\item Phones are pretty much unaffordable, and the modes comparison isn't on solid theoretical footing anyway. Given my finances, my data collection should be entirely online, so scrap paper II and come up with something else
					\end{coi}
				\item Jeff
					\begin{coi}
						\item I spoke to Jeff after I'd heard the above from Matt and Ryan. He agreed with everything Matt and Ryan said. He favored going with Lucid for the online stuff, scrapping paper II, and having MTurk as the fallback option
					\end{coi}
			\end{coi}
		\item Three-pronged strategy going forward:
			\begin{enumerate}
				\item Lucid for online survey
					\begin{coi}
						\item Hire Lucid to recruit people for the online survey with my sequential blocking method
					\end{coi}
				\item Scrap paper II
					\begin{coi}
						\item Scrap paper II on the modes comparison and come up with something else that fits the dissertation outline
					\end{coi}
				\item MTurk
					\begin{coi}
						\item If all else fails, I can do online and phone through MTurk and easily get a receipt for the Provost by April
					\end{coi}
			\end{enumerate}
		\item Definitely 1. and 2.: Lucid and scrap paper II. Use MTurk for the pre-polls, as planned
	\end{coi}



\section*{Making payments and getting reimbursed}
	\begin{coi}
		\item Pay Lucid \$4,662
			\begin{coi}
				\item I don't have that money. Anita Brown was a huge pain and rejected my idea that the Data Science Center pay and get reimbursed for me. After Jeff intervened, the Dean (Jon Tubman) said we can make this work. Below is the outline:
					\begin{coi}
						\item Lucid needs to fill in an application to get approved and added to the AU approved-vendor database
						\item I send that application and the invoice to Edith
						\item Edith mailed a hard-copy check (\# 0107580, \$4,662) on April 1. It should reach Lucid by April 8
						\item Edith works directly with the Controller's office (Nicole Bresnahan) and Financial Aid (Selena Healey) to have SPA reimbursed
						\item Tell Lucid to expect the check in the mail by April 8 at the latest
						\item Oh my. Lucid still had not gotten the check on April 12, so I inquired with Edith again. Turns out the didn't mail a hard-copy check after all but sent the payment electronically with Lucid's ACH information. The person who emailed me, Sheila, gave me the e-number of the payment -- it's 0107580, the same as before. I sent that number to Lucid
						\item Mikayla confirmed the electronic payment receipt via email. It arrived on April 12
						\item I asked Mikayla to send me something on an official form that states that payment for my invoice was received
						\item She sent me a new invoice that states that I have paid and that there is zero outstanding balance due. I saved it under \texttt{lucid\_invoice\_paid}
					\end{coi}
			\end{coi}
		\item Pay MTurk \$168
			\begin{coi}
				\item Put the remaining \$168 on my MTurk account
				\item Submit MTurk receipt to Anita for reimbursement
				\item Anita confirmed and processed MTurk reimbursement on April 9
				\item The money is on my AU student account (as a negative balance)
			\end{coi}
		\item That's it. Payments/Reimbursements are done
	\end{coi}



\end{document}


