\input{/Users/simonheuberger/Dropbox/work/latex/preamble}

\title{Plans Going Forward}

\date{}

\begin{document}

\maketitle

\vspace{-1.6cm}

\section*{Ordinal/Blocking}
	\begin{coi}
		\item The model is trained on the ANES 2016
		\item The \texttt{External data} section blocks the ANES 2016 on the original education categories and runs OLS on a Trump feeling thermometer. It then blocks it on the OP education categories and runs the same OLS. The results are compared
		\item I would like to include more external data to showcase the effect of the different categories. I tried CCES, but their education are virtually identical to the OP-estimated ones, so applying them doesn't change anything. Any ideas/suggestions? 
		\item I would like to include more variations in the response variable. The feeling thermometer is interval. I would like to also use a binary and an ordinal (i.e. Likert) response variable, to show how the different categories affect those variable analyses. Good idea?
		\item I have 2,331 respondents from Lucid. I would like to split the sample in half: One half gets the survey with the original ANES 2016 categories, the other half gets the survey with the OP-estimated categories. That way I can show the difference between the two when blocked and analyzed, just like I do for the external data. That would mean 1,165 per half, split over 5 treatment groups, so 233 per group. Enough? Good idea?
	\end{coi}
	
\section*{Framing}
	\begin{coi}
		\item Meta-analysis
		\item Pre-poll \#1
			\begin{coi}
				\item After meta-analysis is done
				\item 300 respondents, \$0.20 each on MTurk
			\end{coi}
		\item Design gap-filling frames
			\begin{coi}
				\item After pre-poll \#1 is done
			\end{coi}
		\item Pre-poll \#2
			\begin{coi}
				\item After gap-filling frames are designed
				\item 300 respondents, \$0.20 each on MTurk
			\end{coi}
		\item Design questionnaire
		\item New IRB approval
		\item Pre-analysis plan and pre-registration
		\item Analysis of results with ordinal probit
	\end{coi}

\section*{Paper II}
	\begin{coi}
		\item Not looked into yet
		\item Possibility: Missing data
			\begin{coi}
				\item People treat {\tt NA} and {\tt Don't know} as the same thing, but they're not. My online survey would contain {\tt Don't know}, so there could be something there
			\end{coi}
	\end{coi}
	
\section*{Timeline Suggestions}
	\begin{coi}
		\item Blocking written up by June/July (except experiment results)
		\item Framing and paper II pursued simultaneously
		\item Framing pre-analyses done by November
		\item Paper II topic found and researched by December
		\item Run experiment January/February 2020
		\item Analyze results and conduct write-up by May 2020
		\item Final write-up completed by August 2020
	\end{coi}





\end{document}


