\input{/Users/simonheuberger/Dropbox/work/latex/preamble}

\title{Plans Going Forward -- FEEDBACK}

\date{}

\begin{document}

\maketitle

\vspace{-1.6cm}

\section*{Ordinal/Blocking}
	\begin{coi}
		\item I thought my Table 2.2 shows evidence that OP is better than making things numeric. It doesn't. I am using a placebo treatment, i.e. there is no treatment, so the Group T2 coefficient should be zero. In other words: There would be differences with anything here, since it's just one single draw. I need evidence that OP works better
			\begin{coi}
				\item Evidence 1: Monte Carlo simulations
					\begin{coi}
						\item MVN data with some cross-correlations
						\item I know the true treatment effect here
						\item So when I then block on categories 1:15 and 1:5, I know which one performs better -- the one that's closer to the true treatment effect
					\end{coi}
				\item Evidence 2: Repeat the Table 2.2. estimations 100 times and show the distributions around zero
					\begin{coi}
						\item The table is created with a placebo treatment, i.e. there is no real treatment. That means Group T2 should be zero. The table is not evidence that the OP method is better
						\item Repeat the estimations for Table 2.2 100 times and visualize the distribution of the Group T2 coefficients. This will show which category estimation is closer to zero, which is the true value of that coefficient
					\end{coi} 
			\end{coi}
		\item Perform a test to check that OP assigns people correctly
			\begin{coi}
				\item I currently estimate the model, then bin people according to their estimated values, which results in the new categories
				\item Now take the people with their originally selected education categories and manually assign them to the new categories
				\item Then check that the resulting distribution looks the same as the binned-values one
				\item This is a test to ensure that, say, a 4th grade guy, doesn't get binned into, say, Master's, by accident
			\end{coi}
		\item Write up the \texttt{shiny} survey environment in the appendix
		\item Emphasize machine learning in the write-up
			\begin{coi}
				\item Model training is what it's all about
				\item People are being misclassified based on arbitrary numeric values
			\end{coi}
	\end{coi}

\section*{Framing}
	\begin{coi}
		\item Meta-analyses take months, even when you know what you're doing. There is no way I can get any unpublished framing studies, so my results won't mean anything anyway. There is still the huge looming threat of getting absolutely nothing after all this and the pre-polls. And it doesn't fit at all with the blocking paper
		\item Ditch framing. Make the entire dissertation about measurements in surveys
		\item Name this paper II and make it about using ordinal variables as predictors. That fits in nicely with the ordinal blocking
		\item I will still need to run the framing survey, but I am then independent of having to achieve significant results, since I only care about the measurements
	\end{coi}

\section*{Paper III}
	\begin{coi}
		\item Make paper III about missing data
	\end{coi}



\end{document}


