# QUALITY COMPARISON OF MAJOR MISSING DATA SOLUTIONS FOR DISCRETE DATA WITH A PROPOSED NEW METHOD FOR ORDINAL VARIABLES {#ordmiss}

## Introduction {#ordmiss-intro}

```{r include=FALSE}
# function to make all diff columns absolute values
abs.diff <- function(df){
  df$diff <- df$diff %>% abs
  return(df)
}

# function to drop leading zeroes in numeric columns in data frames (adapted
# from f_num()) and add a plus sign for positive values
dropZero.addPlus <- function (df, digits = 4){
  x <- dplyr::select_if(df, is.numeric)
  for(i in 1:ncol(x)){
    x[,i] <- round(as.numeric(x[,i]), digits)
    x[,i] <- sprintf(paste0("%.", digits, "f"), x[,i])
    x[,i] <- gsub("^0(?=\\.)|(?<=-)0", "", x[,i], perl = TRUE)
  }
  df[, colnames(x)] <- x
  
  for(i in 1:nrow(df)){
    if(grepl("-", df$diff[i]) == FALSE){
      df$diff[i] <- paste0("+", df$diff[i])
    }else{
      df$diff[i] <- paste0("-", df$diff[i])
    }
  }
  return(df)
}

drop.zero <- function (df, digits = 4, p, s, pad.char = NA, ...){
    library(dplyr)
    ldots <- list(...)
    if (length(ldots) > 0) {
        if (!is.null(ldots[["prefix"]]) & missing(p)) 
            p <- ldots[["prefix"]]
        if (!is.null(ldots[["suffix"]]) & missing(s)) 
            s <- ldots[["suffix"]]
    }
    x <- dplyr::select_if(df, is.numeric)
    for(i in 1:ncol(x)){
      x[,i] <- round(as.numeric(x[,i]), digits)
      x[,i] <- sprintf(paste0("%.", digits, "f"), x[,i])
      x[,i] <- gsub("^0(?=\\.)|(?<=-)0", "", x[,i], perl = TRUE)
    }
    df[, colnames(x)] <- x
    return(df)
}

```

Missing data are ubiquitous in survey research [@allison_2002_missing;@raghunathan_2016_missing]. Respondents frequently refuse to answer questions, select "Don't Know" as a response option, or drop out during the response collection process [@honaker_2010_what]. Missing data pose a big problem for researchers because data can typically not be analyzed with statistical software if they contain missing values [@little_2002_statistical;@molenberghs_2007_missing]. 

Scholars have developed several general ways to treat missing data. These range from deleting all observations with missing data (listwise deletion) over randomly drawing a 'similar' respondent to provide a fill-in value for a missing slot (hot decking) to estimating missing values from conditional distributions (multiple imputation) [@rubin_1976_inference;@king_2001_analyzing;@fay_1996_alternative]. 

Listwise deletion has been shown to induce bias with political data [@rees_1997_methods;@reilly_1993_data]. +++ more citations, examples of how widely used listwise deletion is

Hot decking does not reflect statistical uncertainty in the filled-in values since there is only one draw [@kroh_2006_taking;@gill_2013_bayesian]. +++ More detail about the method

Multiple implementation has become the state of the art in missing data management +++ citations, examples, reasons why it's the state of the art

However, multiple imputation is not necessarily always the most suitable method for all types of variables. For non-granular discrete data, for instance, multiple hot deck imputation, a variation over generic multiple imputation, proves more precise [@gill_2012_have]. +++ how does it achieve that

However, multiple hot deck imputation assumes even distances between categories in discrete data. This assumption does not necessarily apply for ordinal variables. I propose a method designed to impute discrete missing data specifically from ordinal variables. Because of the success of multiple hot deck imputation, this method is based on multiple hot deck imputation and adapted to account for the specific circumstances of ordinal variables. Based on the ordered probit model approach in chapter II, it applies a weighted distance solution with newly estimated numeric thresholds from an assumed underlying latent continuous variable to measure the distances between the categories and calculate an affinity score.


This chapter will:

-- Provide theory behind missing data mechanisms, deletion, imputation, multiple imputation
-- Outline `R` packages/functions that implement listwise deletion and variations of multiple imputation, including my proposed new method
  -- `na.omit()`
  -- `amelia()`
  -- `mice()`
  -- `hot.deck()`
  -- `hd.ord()`
-- Apply these `R` packages to three different sets of survey data
-- Test each package for accuracy and speed for differing types of variables
-- Assess the usefulness of my proposed new method


## Theory {#ordmiss-theory}

### Missing Data Mechanisms {#ordmiss-theory-mechanisms}

MCAR
MAR
NMAR


### Deletion {#ordmiss-theory-delete}

Deletion of incomplete observations, listwise deletion


### Imputation {#ordmiss-theory-impute}

#### Mean {#ordmiss-theory-impute-mean}

Mean is used to substitute values


#### Regression {#ordmiss-theory-impute-regress}

Missing variables for a unit are estimated by predicted values from the regression on the known variables for that unit


#### Hot Decking {#ordmiss-theory-impute-hd}

Recorded units in the sample are used to substitute values

Hot decking (Marker, Juddkins, Winglee (2002), Ernst (198), Kalton and Kish (1981), Ford (1983), David et al. (1986)) (chapter 4, [@little_2002_statistical])
-- by simple random sampling with replacement
-- within adjustment cells
-- nearest neighbor
-- sequential ordered by a covariate

`R` package: +++


### Multiple Imputation {#ordmiss-theory-multimpute}

#### `Amelia` {#ordmiss-theory-multimpute-amelia}

#### `mice` {#ordmiss-theory-multimpute-mice}

#### Multiple Hot Deck Imputation {#ordmiss-theory-multimpute-hdnorm}

`R` package: `hot.deck`

Multiple hot deck imputation (all COPIED OVER from Cranmer, Gill):
-- A non-parametric alternative to multiple imputation
-- A variation of hot deck imputation combined with the repeated imputation and estimation method typical of parametric multiple imputation
-- Designed to work well in situations where (traditional) parametric multiple imputation falls short -- when a discrete variable with a small number of categories has missing values. This can produce nonsensical imputations, biased results and artificially smaller standard errors
-- Maintains the integrity of the data by using draws of actual values from the variable with the missing values to impute missing items
-- Maintains the discrete nature of discrete data and produces more accurate imputations than parametric multiple imputation in a majority of social science applications where the data are discrete
-- Since many political science applications rely on highly discrete measures, multiple hot deck imputation provides the researcher with more accuracy in imputations than parametric multiple imputation, while requiring none of parametric multiple imputation's standard assumptions

Concrete estimation steps:
(1) Create several copies of the dataset.
(2) Search down columns of the data sequentially looking for missing observations
  a) When a missing value is found, compute a vector of affinity scores, for that missing value. This vector is as long as the number of rows in the dataset, minus any rows with missing values for the same variable
  b) Create the imputation cell of best donors for this missing value and draw randomly from it to produce a vector of imputations
  c) Impute one of these values into the appropriate cell of each duplicate dataset for this missing value
(3) Repeat Step 2 until no missing observations remain
(4) Fit the statistic of interest for each dataset
(5) Combine the estimates of the statistic into a single estimate using the combination rules of parametric multiple imputation


#### Ordinal Variable Multiple Hot Deck Imputation {#ordmiss-theory-multimpute-hdord}

Imputation techniques rely on continuous distributional assumptions.
I use my ordered probit estimated latent underlying continuous variable.

Ordinal hot deck imputation: 
-- An extension of multiple hot deck imputation
-- Designed specifically to implement multiple hot deck imputation with ordinal variables
-- Fully utilizes the unevenly spaced yet ordered information provided in ordinal variables
-- A key variable in political science surveys is ordinal: Education. Ordinal hot deck imputation enables researchers to impute missing data using the full information provided in this most important predictor variable

Multiple hot deck imputation uses draws of values from the variable with the missing values (hot decking) to impute them distributionally (multiple imputation) and estimate affinity scores. This score measures how close other respondents are to the one with the missing value. 'Closeness' is measured as the distance between respondents in the variables that do not contain missing values. This is best illustrated with simplified data shown in Table \ref{ordmiss-affscore}.

\begin{table}[ht]
  \centering
  \begin{tabular}{lccccc}
  \bottomrule 
  \midrule
  Respondent & Age & Party ID & Education & Income & Gender\\
  \hline
  A & 25 & Republican & High School Graduate & \$40-50,000 & Male \\
  B & 40 & NA & Some High School &  \$30-40,000 & Female\\
  C & 30 & Democrat & Bachelor's Degree &  \$60-70,000 & Female\\
  \bottomrule 
  \end{tabular}
  \caption{Illustrative Data}
  \label{ordmiss-affscore}
\end{table}

Respondent B shows missing data for party ID. To impute a fill-in value, we look at how close respondents A and C are to B in terms of age, education, income, and gender. C is closer to B in terms of age and they share the same gender. A is closer to B on education and income. Multiple hot deck imputation measures these distances and estimates affinity scores for respondents A and C. B then receives the party ID fill-in value from whichever respondent has the higher score. The algorithm building the affinity score, however, assumes evenly spaced distances between categories. This is the case for age, income, and gender, but not for education, since education is an ordinal variable. Applying multiple hot deck imputation here would misrepresent the data.

`R` functions: `hd.ord()`

`education` is crucial to test the performance of `hd.ord`, which was designed specifically for ordinal variables. `hd.ord` in turn depends on another specifically designed function called `OPMOrd`. `OPMOrd` applies `polr()` to an ordinal variable (here `education`) to estimate the underlying latent continuous variable. `polr()` can only be run on data without missing variables. +++



## Data {#ordmiss-data}

I ampute data for three different sets of survey data: An experiment on moral framing I ran on MTurk in 2017 (original data), data from the 2016 ANES, and data from the 2016 CCES. All data are amputed with the `ampute()` function from the `mice` package (+++ some citation that talks about ampute here). Each data set is imputed with five different functions: `amelia()`, `mice()`, `hd.ord()`, `hot.deck()`, and `na.omit()`.

`amelia()` is from the `Amelia` package. `mice()` is from the `mice` package. Both are used with their default settings unless specified otherwise. `hot.deck()` is from Gill and Cranmer's multiple hot deck imputation package `hot.deck`. `hd.ord()` is my ordinal variable adaptation of `hot.deck()`. `na.omit()` applies list-wise deletion. I test each function for imputation accuracy and speed for binary, ordinal, and nominal variables in all three data sets. Each data set contains two ordinal (`Education`, `Interest`), two nominal (`Age`, `Income`) and numerous binary variables. In order to enable factually accurate comparison and unless specified otherwise, each data set contains 1,000 observations and six levels of the ordinal variable `Education`. 1,000 observations represent a common size for survey experiment data, and the `polr()` analysis from section \ref{ordblock-data} estimates five or six levels to best represent `Education` in a US context. Imputation of each data set was carried out with each of the five imputation methods for 1,000 iterations. With the exception of Table \ref{mar.5var.old.frame}, 20 percent NA were randomly amputed in each iteration for each data set.

Sections \ref{ordmiss-results-mar} to \ref{ordmiss-results-increaseNA} show the results in terms of performance accuracy. Since each data set is complete, we know the true variable mean of all variables. This serves as the baseline of comparison for the performance of each imputation method. First, I impute all data sets MAR (section \ref{ordmiss-results-mar}) and MNAR (section \ref{ordmiss-results-mnar}) for five and 12 amputed variables. The five amputed variables are consistent across all three data sets: `Democrat` (binary), `Male` (binary), `Interest` (ordinal), `Income` (nominal), and `Age` (nominal). The 12 amputed variables contain additional variables that differ between each data set due to availability in the data. In section \ref{ordmiss-results-increaseOrd}, I then increase the number of ordinal variables to be treated by `polr()` for `hd.ord()` by including `Interest`. Imputations also also conducted MAR and MNAR for four and 11 amputed variables. The variables are the same as in sections \ref{ordmiss-results-mar} and \ref{ordmiss-results-mnar}, but without including `Interest`. Finally, I increase the amount of missing data to 50 and 80 percent (section \ref{ordmiss-results-increaseNA}).

Section \ref{ordmiss-results-speed} shows the results in terms of performance speed by the number of imputed variables (Table \ref{runtimes5var12var}) and the percentage of missingness (Table \ref{run.all.perc}). All running times were achieved on a Code Ocean AWS EC2 instance with 16 cores and 120 GB of memory.




## Results {#ordmiss-results}

<!-- ---- MAIN TEXT ---- -->

<!-- MAR  -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- 12 variables: Dem, Male, Interest, Inc, Age, Black, Empl + 5 selected -->

<!-- MNAR -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- 12 variables: Dem, Male, Interest, Inc, Age, Black, Empl + 5 selected -->

<!-- INCREASED ORDINAL VARIABLES (DVs: educ, interest): -->
<!-- MAR -->
<!-- 4 variables: Dem, Male, Inc, Age -->
<!-- 11 variables: Dem, Male, Inc, Age, Black, Empl + 5 selected -->

<!-- MNAR -->
<!-- 4 variables: Dem, Male, Inc, Age -->
<!-- 11 variables: Dem, Male, Inc, Age, Black, Empl + 5 selected -->

<!-- INCREASED MISSINGNESS (MAR, 20, 50, 80 percent): -->
<!-- Framing, 1000 iterations, 5 variables: Dem, Male, Interest, Inc, Age -->

<!-- SPEED: -->
<!-- MAR 5 variables, MAR 12 variables -->
<!-- MAR 20, 50, 80 percent framing -->



<!-- ---- APPENDIX ---- -->

<!-- ALL OBSERVATIONS (section \ref{app-ordmiss-allObs}): -->
<!-- ANES all obs. 1000 iterations, CCES all obs. 10 iterations (maxed out RAM) -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR (Table \ref{mar.5var.all}) and MNAR (\ref{mnar.5var.all}) -->


<!-- INCREASED MISSINGNESS (section \ref{app-ordmiss-increaseNA}): -->
<!-- CCES 10,000 iterations -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR -->
<!-- 20, 50, 80 percent -->


<!-- SPEED (section \ref{app-ordmiss-speed}): -->
<!-- CCES 10,000 iterations -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR -->
<!-- 20, 50, 80 percent -->

<!-- ANES all obs. 1000 iterations, CCES all obs. 10 iterations (maxed out RAM) -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR -->






### MAR {#ordmiss-results-mar}

```{r Levels Overall, include=FALSE}
levs <- c("amelia", "hot.deck", "hd.ord", "mice", "na.omit", "true")
col.names <- c("Method", "Variable", "ANES", "CCES", "Framing")
```


```{r MAR 5 Variables, include=FALSE}

mar.5var.anes <- read.csv("data/anes/mar/results/anes.mar.results.5var.1000n.1000it.20perc.csv")  %>% .[,-1] %>% dropZero.addPlus
mar.5var.cces <- read.csv("data/cces/mar/results/cces.mar.results.5var.1000n.1000it.20perc.csv")  %>% .[,-1] %>% dropZero.addPlus
mar.5var.frame <- read.csv("data/framing/mar/results/framing.mar.results.5var.1000n.1000it.20perc.csv")  %>% .[,-1] %>% dropZero.addPlus

mar.5var.anes$diff[mar.5var.anes$method == "true"] <- mar.5var.anes$value[mar.5var.anes$method == "true"]
mar.5var.cces$diff[mar.5var.cces$method == "true"] <- mar.5var.cces$value[mar.5var.cces$method == "true"]
mar.5var.frame$diff[mar.5var.frame$method == "true"] <- mar.5var.frame$value[mar.5var.frame$method == "true"]

levels(mar.5var.anes$method) <- levels(mar.5var.cces$method) <- levels(mar.5var.frame$method) <-
  levs

mar.5var <- cbind(mar.5var.anes[, c(1,2,4)], mar.5var.cces[,4], mar.5var.frame[,4])
colnames(mar.5var) <- col.names

# to make the in-text citations shorter
mar.5.anes <- mar.5var$ANES
mar.5.cces <- mar.5var$CCES
mar.5.frame <- mar.5var$Framing
mar.5.meth <- mar.5var$Method
mar.5.var <- mar.5var$Variable

stargazer(mar.5var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MAR, 5 Variables with NA",
          label = "mar.5var")

```






\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. MAR, 5 Variables with NA} 
  \label{mar.5var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0010} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0011} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0008} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0004} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0290} & \multicolumn{1}{c}{--.0229} & \multicolumn{1}{c}{--.0340} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0013} & \multicolumn{1}{c}{--.0011} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0013} & \multicolumn{1}{c}{--.0014} & \multicolumn{1}{c}{+.0005} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0392} & \multicolumn{1}{c}{--.0414} & \multicolumn{1}{c}{--.0256} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0130} & \multicolumn{1}{c}{--.0125} & \multicolumn{1}{c}{--.0213} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0191} & \multicolumn{1}{c}{--.0196} & \multicolumn{1}{c}{--.0248} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0705} & \multicolumn{1}{c}{--.0724} & \multicolumn{1}{c}{--.0714} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1068} & \multicolumn{1}{c}{--.0259} & \multicolumn{1}{c}{--.0119} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1278} & \multicolumn{1}{c}{--.0407} & \multicolumn{1}{c}{--.0192} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0008} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{+.0014} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.5631} & \multicolumn{1}{c}{--.2468} & \multicolumn{1}{c}{--.1367} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3888} & \multicolumn{1}{c}{--.2616} & \multicolumn{1}{c}{--.3650} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.4597} & \multicolumn{1}{c}{--.3895} & \multicolumn{1}{c}{--.3923} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0007} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{--.0039} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0017} & \multicolumn{1}{c}{--.0073} & \multicolumn{1}{c}{--.0049} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--1.1875} & \multicolumn{1}{c}{--1.2361} & \multicolumn{1}{c}{--1.0641} \\
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean.}
\end{tablenotes}
\end{threeparttable}
\end{table} 





\clearpage

```{r MAR 12 Variables, include=FALSE}

mar.12var.anes <- read.csv("data/anes/mar/results/anes.mar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mar.12var.cces <- read.csv("data/cces/mar/results/cces.mar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mar.12var.frame<- read.csv("data/framing/mar/results/framing.mar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mar.12var.anes$diff[mar.12var.anes$method == "true"] <- mar.12var.anes$value[mar.12var.anes$method == "true"]
mar.12var.cces$diff[mar.12var.cces$method == "true"] <- mar.12var.cces$value[mar.12var.cces$method == "true"]
mar.12var.frame$diff[mar.12var.frame$method == "true"] <- mar.12var.frame$value[mar.12var.frame$method == "true"]

levels(mar.12var.anes$method) <- levels(mar.12var.cces$method) <- levels(mar.12var.frame$method) <-
  levs

un.meth <- mar.12var.anes$method %>% unique
un.meth.len <- un.meth %>% length
un.vars <- c(mar.12var.anes$variable %>% as.character,
                 mar.12var.cces$variable %>% as.character, 
                 mar.12var.frame$variable %>% as.character) %>%
  unique
un.vars.len <- un.vars %>% length
un.anes.len <- mar.12var.anes$variable %>% unique %>% length
un.cces.var <- mar.12var.cces$variable %>% unique %>% as.character
un.cces.len <- un.cces.var %>% length
un.frame.var <- mar.12var.frame$variable %>% unique %>% as.character
un.frame.len <- un.frame.var %>% length
Variable <- rep(un.vars, each = un.meth.len)
Method <- rep(un.meth, un.vars.len) %>% as.character
meth.len <- Method %>% length

mar.12var <- cbind(Method, Variable) %>% as.data.frame

mar.12var$mar.anes.col <- c(mar.12var.anes$diff, 
                            rep("---", 
                                un.meth.len * (un.vars.len - un.anes.len)))
mar.12var$mar.cces.col <- rep("---", meth.len) %>% as.character
mar.12var$mar.frame.col <- rep("---", meth.len) %>% as.character

for(i in 1:(un.cces.len)){
  mar.12var$mar.cces.col[mar.12var$Variable == un.cces.var[i]] <- mar.12var.cces$diff[mar.12var.cces$variable == un.cces.var[i]]
  mar.12var$mar.frame.col[mar.12var$Variable == un.frame.var[i]] <- mar.12var.frame$diff[mar.12var.frame$variable == un.frame.var[i]]
}

colnames(mar.12var) <- col.names

# to make the in-text citations shorter
mar.12.anes <- mar.12var$ANES
mar.12.cces <- mar.12var$CCES
mar.12.frame <- mar.12var$Framing
mar.12.meth <- mar.12var$Method
mar.12.var <- mar.12var$Variable

stargazer(mar.12var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MAR, 12 Variables with NA",
          label = "mar.12var")

```

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. MAR, 12 Variables with NA} 
  \label{mar.12var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0004} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0191} & \multicolumn{1}{c}{--.0172} & \multicolumn{1}{c}{--.0280} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0256} & \multicolumn{1}{c}{--.0364} & \multicolumn{1}{c}{--.0154} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0095} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0077} & \multicolumn{1}{c}{--.0067} & \multicolumn{1}{c}{--.0106} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0620} & \multicolumn{1}{c}{--.0515} & \multicolumn{1}{c}{--.0721} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0470} & \multicolumn{1}{c}{--.0130} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0591} & \multicolumn{1}{c}{--.0212} & \multicolumn{1}{c}{--.0089} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0007} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0013} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.6303} & \multicolumn{1}{c}{--.2860} & \multicolumn{1}{c}{--.0960} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1391} & \multicolumn{1}{c}{--.0883} & \multicolumn{1}{c}{--.1494} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1835} & \multicolumn{1}{c}{--.1435} & \multicolumn{1}{c}{--.1592} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0056} & \multicolumn{1}{c}{--.0015} & \multicolumn{1}{c}{--.0041} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0048} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0029} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.8638} & \multicolumn{1}{c}{--.5974} & \multicolumn{1}{c}{--.6434} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0092} & \multicolumn{1}{c}{--.0090} & \multicolumn{1}{c}{--.0110} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0006} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0007} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0006} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0006} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0087} & \multicolumn{1}{c}{--.0301} & \multicolumn{1}{c}{--.0157} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0006} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0166} & \multicolumn{1}{c}{--.0234} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0384} & \multicolumn{1}{c}{--.0326} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0334} & \multicolumn{1}{c}{--.0304} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0191} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0320} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0112} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0117} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0072} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0385} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0049} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0984} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0021} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.1003} \\ 
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize





### MNAR {#ordmiss-results-mnar}

```{r MNAR 5 Variables, include=FALSE}

mnar.5var.anes <- read.csv("data/anes/mnar/results/anes.mnar.results.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.5var.cces <- read.csv("data/cces/mnar/results/cces.mnar.results.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.5var.frame <- read.csv("data/framing/mnar/results/framing.mnar.results.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mnar.5var.anes$diff[mnar.5var.anes$method == "true"] <- mnar.5var.anes$value[mnar.5var.anes$method == "true"]
mnar.5var.cces$diff[mnar.5var.cces$method == "true"] <- mnar.5var.cces$value[mnar.5var.cces$method == "true"]
mnar.5var.frame$diff[mnar.5var.frame$method == "true"] <- mnar.5var.frame$value[mnar.5var.frame$method == "true"]

levels(mnar.5var.anes$method) <- levels(mnar.5var.cces$method) <- levels(mnar.5var.frame$method) <-
  levs

mnar.5var <- cbind(mnar.5var.anes[,c(1,2,4)], mnar.5var.cces[,4], mnar.5var.frame[,4])
colnames(mnar.5var) <- col.names

# to make the in-text citations shorter
mnar.5.anes <- mnar.5var$ANES
mnar.5.cces <- mnar.5var$CCES
mnar.5.frame <- mnar.5var$Framing
mnar.5.meth <- mnar.5var$Method
mnar.5.var <- mnar.5var$Variable

stargazer(mnar.5var,
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MNAR, 5 Variables with NA",
          label = "mnar.5var")

```


\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. MNAR, 5 Variables with NA} 
  \label{mnar.5var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0114} & \multicolumn{1}{c}{--.0099} & \multicolumn{1}{c}{--.0038} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0120} & \multicolumn{1}{c}{--.0105} & \multicolumn{1}{c}{--.0033} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0106} & \multicolumn{1}{c}{--.0102} & \multicolumn{1}{c}{--.0046} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0099} & \multicolumn{1}{c}{--.0101} & \multicolumn{1}{c}{--.0036} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0176} & \multicolumn{1}{c}{--.0140} & \multicolumn{1}{c}{--.0185} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0136} & \multicolumn{1}{c}{--.0116} & \multicolumn{1}{c}{--.0127} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0133} & \multicolumn{1}{c}{--.0124} & \multicolumn{1}{c}{--.0125} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0132} & \multicolumn{1}{c}{--.0121} & \multicolumn{1}{c}{--.0133} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0132} & \multicolumn{1}{c}{--.0120} & \multicolumn{1}{c}{--.0135} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0214} & \multicolumn{1}{c}{--.0219} & \multicolumn{1}{c}{--.0133} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0288} & \multicolumn{1}{c}{--.0246} & \multicolumn{1}{c}{--.0333} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0335} & \multicolumn{1}{c}{--.0296} & \multicolumn{1}{c}{--.0369} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0167} & \multicolumn{1}{c}{--.0146} & \multicolumn{1}{c}{--.0133} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0167} & \multicolumn{1}{c}{--.0146} & \multicolumn{1}{c}{--.0135} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0379} & \multicolumn{1}{c}{--.0372} & \multicolumn{1}{c}{--.0379} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2299} & \multicolumn{1}{c}{--.0928} & \multicolumn{1}{c}{--.0591} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2554} & \multicolumn{1}{c}{--.1038} & \multicolumn{1}{c}{--.0648} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1225} & \multicolumn{1}{c}{--.0578} & \multicolumn{1}{c}{--.0463} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1229} & \multicolumn{1}{c}{--.0566} & \multicolumn{1}{c}{--.0445} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2770} & \multicolumn{1}{c}{--.1334} & \multicolumn{1}{c}{--.0740} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6319} & \multicolumn{1}{c}{--.4596} & \multicolumn{1}{c}{--.7147} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.7415} & \multicolumn{1}{c}{--.5929} & \multicolumn{1}{c}{--.7477} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2450} & \multicolumn{1}{c}{--.2266} & \multicolumn{1}{c}{--.2875} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2369} & \multicolumn{1}{c}{--.2160} & \multicolumn{1}{c}{--.2888} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6427} & \multicolumn{1}{c}{--.6392} & \multicolumn{1}{c}{--.5853} \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean.}
\end{tablenotes}
\end{threeparttable}
\end{table}




\clearpage

```{r MNAR 12 Variables, include=FALSE}

mnar.12var.anes <- read.csv("data/anes/mnar/results/anes.mnar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.12var.cces <- read.csv("data/cces/mnar/results/cces.mnar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.12var.frame <- read.csv("data/framing/mnar/results/framing.mnar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mnar.12var.anes$diff[mnar.12var.anes$method == "true"] <- mnar.12var.anes$value[mnar.12var.anes$method == "true"]
mnar.12var.cces$diff[mnar.12var.cces$method == "true"] <- mnar.12var.cces$value[mnar.12var.cces$method == "true"]
mnar.12var.frame$diff[mnar.12var.frame$method == "true"] <- mnar.12var.frame$value[mnar.12var.frame$method == "true"]

levels(mnar.12var.anes$method) <- levels(mnar.12var.cces$method) <- levels(mnar.12var.frame$method) <-
  levs

# there are several in-between code steps that are identical to MAR 12 Variables
# above, so I didn't include them here

mnar.12var <- cbind(Method, Variable) %>% as.data.frame

mnar.12var$mnar.anes.col <- c(mnar.12var.anes$diff,
                              rep("---",
                                  un.meth.len * (un.vars.len - un.anes.len)))
mnar.12var$mnar.cces.col <- rep("---", meth.len) %>% as.character
mnar.12var$mnar.frame.col <- rep("---", meth.len) %>% as.character

for(i in 1:(un.cces.len)){
  mnar.12var$mnar.cces.col[mnar.12var$Variable == un.cces.var[i]] <- mnar.12var.cces$diff[mnar.12var.cces$variable == un.cces.var[i]]
  mnar.12var$mnar.frame.col[mnar.12var$Variable == un.frame.var[i]] <- mnar.12var.frame$diff[mnar.12var.frame$variable == un.frame.var[i]]
}

colnames(mnar.12var) <- col.names

# to make the in-text citations shorter
mnar.12.anes <- mnar.12var$ANES
mnar.12.cces <- mnar.12var$CCES
mnar.12.frame <- mnar.12var$Framing
meth <- mnar.12var$Method
varb <- mnar.12var$Variable

stargazer(mnar.12var,
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MNAR, 12 Variables with NA",
          label = "mnar.12var")

```

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. MNAR, 12 Variables with NA} 
  \label{mnar.12var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0046} & \multicolumn{1}{c}{--.0015} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0013} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0018} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0014} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0092} & \multicolumn{1}{c}{--.0081} & \multicolumn{1}{c}{--.0106} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0052} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0051} & \multicolumn{1}{c}{--.0051} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0055} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0093} & \multicolumn{1}{c}{--.0119} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0113} & \multicolumn{1}{c}{--.0090} & \multicolumn{1}{c}{--.0139} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0134} & \multicolumn{1}{c}{--.0113} & \multicolumn{1}{c}{--.0150} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0068} & \multicolumn{1}{c}{--.0061} & \multicolumn{1}{c}{--.0053} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0068} & \multicolumn{1}{c}{--.0061} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0236} & \multicolumn{1}{c}{--.0161} & \multicolumn{1}{c}{--.0252} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0899} & \multicolumn{1}{c}{--.0350} & \multicolumn{1}{c}{--.0239} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1046} & \multicolumn{1}{c}{--.0421} & \multicolumn{1}{c}{--.0262} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0495} & \multicolumn{1}{c}{--.0223} & \multicolumn{1}{c}{--.0184} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0503} & \multicolumn{1}{c}{--.0218} & \multicolumn{1}{c}{--.0177} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2088} & \multicolumn{1}{c}{--.0970} & \multicolumn{1}{c}{--.0333} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2571} & \multicolumn{1}{c}{--.1732} & \multicolumn{1}{c}{--.2811} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3081} & \multicolumn{1}{c}{--.2251} & \multicolumn{1}{c}{--.2989} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1100} & \multicolumn{1}{c}{--.1014} & \multicolumn{1}{c}{--.1159} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1047} & \multicolumn{1}{c}{--.0986} & \multicolumn{1}{c}{--.1159} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3397} & \multicolumn{1}{c}{--.1367} & \multicolumn{1}{c}{--.2239} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0035} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{--.0028} \\
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{--.0029} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0011} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0034} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{--.0010} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0052} & \multicolumn{1}{c}{--.0045} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0034} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0031} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0031} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0014} & \multicolumn{1}{c}{--.0111} & \multicolumn{1}{c}{--.0037} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} \\
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0073} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{--.0096} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0028} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0111} & \multicolumn{1}{c}{--.0090} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0077} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0051} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0048} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0024} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0024} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0035} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0051} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0070} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0011} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0010} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0033} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0049} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0048} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0142} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0023} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0020} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0017} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0142} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0152} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0101} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0101} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0363} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0115} \\
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0115} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0099} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0094} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0358} \\ 
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize




### Increased Ordinal Variables {#ordmiss-results-increaseOrd}


```{r MULT MAR 4 Variables, include=FALSE}

mult.mar.4var.anes <- read.csv("data/anes/mar/results/anes.mar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.4var.cces <- read.csv("data/cces/mar/results/cces.mar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.4var.frame <- read.csv("data/framing/mar/results/framing.mar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mar.4var.anes$diff[mult.mar.4var.anes$method == "true"] <- mult.mar.4var.anes$value[mult.mar.4var.anes$method == "true"]
mult.mar.4var.cces$diff[mult.mar.4var.cces$method == "true"] <- mult.mar.4var.cces$value[mult.mar.4var.cces$method == "true"]
mult.mar.4var.frame$diff[mult.mar.4var.frame$method == "true"] <- mult.mar.4var.frame$value[mult.mar.4var.frame$method == "true"]

levels(mult.mar.4var.anes$method) <- levels(mult.mar.4var.cces$method) <- levels(mult.mar.4var.frame$method) <-
  levs

mult.mar.4var <- cbind(mult.mar.4var.anes[, c(1,2,4)], mult.mar.4var.cces[,4], mult.mar.4var.frame[,4])
colnames(mult.mar.4var) <- col.names

# to make the in-text citations shorter
mult.mar.4.anes <- mult.mar.4var$ANES
mult.mar.4.cces <- mult.mar.4var$CCES
mult.mar.4.frame <- mult.mar.4var$Framing
mult.mar.4.meth <- mult.mar.4var$Method
mult.mar.4.varb <- mult.mar.4var$Variable

stargazer(mult.mar.4var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 4 Variables with NA",
          label = "mult.mar.4var")

```


\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 4 Variables with NA} 
  \label{mult.mar.4var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0008} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0005} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0018} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{+.0012} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0333} & \multicolumn{1}{c}{--.0294} & \multicolumn{1}{c}{--.0357} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0022} & \multicolumn{1}{c}{--.0019} & \multicolumn{1}{c}{+.0015} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0015} & \multicolumn{1}{c}{--.0018} & \multicolumn{1}{c}{+.0011} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0396} & \multicolumn{1}{c}{--.0407} & \multicolumn{1}{c}{--.0297} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0830} & \multicolumn{1}{c}{--.0246} & \multicolumn{1}{c}{--.0093} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1523} & \multicolumn{1}{c}{--.0516} & \multicolumn{1}{c}{--.0225} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0010} & \multicolumn{1}{c}{--.0006} & \multicolumn{1}{c}{+.0009} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0008} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0020} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.5771} & \multicolumn{1}{c}{--.2564} & \multicolumn{1}{c}{--.1400} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2889} & \multicolumn{1}{c}{--.2350} & \multicolumn{1}{c}{--.3546} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.5431} & \multicolumn{1}{c}{--.4664} & \multicolumn{1}{c}{--.4583} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0018} & \multicolumn{1}{c}{+.0085} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0024} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--1.1521} & \multicolumn{1}{c}{--1.1228} & \multicolumn{1}{c}{--.9688} \\  
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean.}
\end{tablenotes}
\end{threeparttable}
\end{table}


\clearpage

```{r MULT MAR 11 Variables, include=FALSE}

mult.mar.11var.anes <- read.csv("data/anes/mar/results/anes.mar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.11var.cces <- read.csv("data/cces/mar/results/cces.mar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.11var.frame <- read.csv("data/framing/mar/results/framing.mar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mar.11var.anes$diff[mult.mar.11var.anes$method == "true"] <- mult.mar.11var.anes$value[mult.mar.11var.anes$method == "true"]
mult.mar.11var.cces$diff[mult.mar.11var.cces$method == "true"] <- mult.mar.11var.cces$value[mult.mar.11var.cces$method == "true"]
mult.mar.11var.frame$diff[mult.mar.11var.frame$method == "true"] <- mult.mar.11var.frame$value[mult.mar.11var.frame$method == "true"]

levels(mult.mar.11var.anes$method) <- levels(mult.mar.11var.cces$method) <- levels(mult.mar.11var.frame$method) <-
  levs


mult.un.meth <- mult.mar.11var.anes$method %>% unique
mult.un.meth.len <- mult.un.meth %>% length
mult.un.vars <- c(mult.mar.11var.anes$variable %>% as.character,
                  mult.mar.11var.cces$variable %>% as.character,
                  mult.mar.11var.frame$variable %>% as.character) %>%
  unique
mult.un.vars.len <- mult.un.vars %>% length
mult.un.anes.len <- mult.mar.11var.anes$variable %>% unique %>% length
mult.un.cces.var <- mult.mar.11var.cces$variable %>% unique %>% as.character
mult.un.cces.len <- mult.un.cces.var %>% length
mult.un.frame.var <- mult.mar.11var.frame$variable %>% unique %>% as.character
mult.un.frame.len <- mult.un.frame.var %>% length

mult.variable <- rep(mult.un.vars, each = mult.un.meth.len)
mult.method <- rep(mult.un.meth, mult.un.vars.len) %>% as.character
mult.meth.len <- mult.method %>% length

mult.mar.11var <- cbind(mult.method, mult.variable) %>% as.data.frame

mult.mar.11var$mult.anes.col <- c(mult.mar.11var.anes$diff,
                                  rep("---",
                                      mult.un.meth.len * (mult.un.vars.len - mult.un.anes.len)))
mult.mar.11var$mult.cces.col <- rep("---", mult.meth.len) %>% as.character
mult.mar.11var$mult.frame.col <- rep("---", mult.meth.len) %>% as.character

for(i in 1:(mult.un.cces.len)){
  mult.mar.11var$mult.cces.col[mult.mar.11var$mult.variable == mult.un.cces.var[i]] <- mult.mar.11var.cces$diff[mult.mar.11var.cces$variable == mult.un.cces.var[i]]
  mult.mar.11var$mult.frame.col[mult.mar.11var$mult.variable == mult.un.frame.var[i]] <- mult.mar.11var.frame$diff[mult.mar.11var.frame$variable == mult.un.frame.var[i]]
}

colnames(mult.mar.11var) <- col.names

# to make the in-text citations shorter
mult.mar.11.anes <- mult.mar.11var$ANES
mult.mar.11.cces <- mult.mar.11var$CCES
mult.mar.11.frame <- mult.mar.11var$Framing
mult.mar.11.meth <- mult.mar.11var$Method
mult.mar.11.varb <- mult.mar.11var$Variable

stargazer(mult.mar.11var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 11 Variables with NA",
          label = "mult.mar.11var")


```

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 11 Variables with NA} 
  \label{mult.mar.11var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{+.0005} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0200} & \multicolumn{1}{c}{--.0213} & \multicolumn{1}{c}{--.0294} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0254} & \multicolumn{1}{c}{--.0350} & \multicolumn{1}{c}{--.0174} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0346} & \multicolumn{1}{c}{--.0114} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0657} & \multicolumn{1}{c}{--.0241} & \multicolumn{1}{c}{--.0095} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0018} & \multicolumn{1}{c}{--.0007} & \multicolumn{1}{c}{--.0004} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.6432} & \multicolumn{1}{c}{--.2888} & \multicolumn{1}{c}{--.0983} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0887} & \multicolumn{1}{c}{--.0704} & \multicolumn{1}{c}{--.1379} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1951} & \multicolumn{1}{c}{--.1532} & \multicolumn{1}{c}{--.1640} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0010} & \multicolumn{1}{c}{--.0021} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0016} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{+.0022} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.8025} & \multicolumn{1}{c}{--.4330} & \multicolumn{1}{c}{--.5290} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0103} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{--.0134} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0007} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0008} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0008} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0007} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0109} & \multicolumn{1}{c}{--.0328} & \multicolumn{1}{c}{--.0159} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0174} & \multicolumn{1}{c}{--.0241} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0390} & \multicolumn{1}{c}{--.0324} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0341} & \multicolumn{1}{c}{--.0295} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0186} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0007} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0310} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0113} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0146} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0091} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0006} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0004} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0373} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0047} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0059} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0921} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0019} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0963} \\
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize



```{r MULT MNAR 4 Variables, include=FALSE}

mult.mnar.4var.anes <- read.csv("data/anes/mnar/results/anes.mnar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.4var.cces <- read.csv("data/cces/mnar/results/cces.mnar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.4var.frame <- read.csv("data/framing/mnar/results/framing.mnar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mnar.4var.anes$diff[mult.mnar.4var.anes$method == "true"] <- mult.mnar.4var.anes$value[mult.mnar.4var.anes$method == "true"]
mult.mnar.4var.cces$diff[mult.mnar.4var.cces$method == "true"] <- mult.mnar.4var.cces$value[mult.mnar.4var.cces$method == "true"]
mult.mnar.4var.frame$diff[mult.mnar.4var.frame$method == "true"] <- mult.mnar.4var.frame$value[mult.mnar.4var.frame$method == "true"]

levels(mult.mnar.4var.anes$method) <- levels(mult.mnar.4var.cces$method) <- levels(mult.mnar.4var.frame$method) <-
  levs

mult.mnar.4var <- cbind(mult.mnar.4var.anes[, c(1,2,4)], mult.mnar.4var.cces[,4], mult.mnar.4var.frame[,4])
colnames(mult.mnar.4var) <- col.names

# to make the in-text citations shorter
mult.mnar.4.anes <- mult.mnar.4var$ANES
mult.mnar.4.cces <- mult.mnar.4var$CCES
mult.mnar.4.frame <- mult.mnar.4var$Framing
mult.mnar.4.meth <- mult.mnar.4var$Method
mult.mnar.4.varb <- mult.mnar.4var$Variable

stargazer(mult.mnar.4var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 4 Variables with NA",
          label = "mult.mnar.4var")


```



\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 4 Variables with NA} 
  \label{mult.mnar.4var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0142} & \multicolumn{1}{c}{--.0133} & \multicolumn{1}{c}{--.0043} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0155} & \multicolumn{1}{c}{--.0131} & \multicolumn{1}{c}{--.0042} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0136} & \multicolumn{1}{c}{--.0131} & \multicolumn{1}{c}{--.0059} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0127} & \multicolumn{1}{c}{--.0130} & \multicolumn{1}{c}{--.0046} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0211} & \multicolumn{1}{c}{--.0185} & \multicolumn{1}{c}{--.0207} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0180} & \multicolumn{1}{c}{--.0162} & \multicolumn{1}{c}{--.0167} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0172} & \multicolumn{1}{c}{--.0160} & \multicolumn{1}{c}{--.0157} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0170} & \multicolumn{1}{c}{--.0154} & \multicolumn{1}{c}{--.0170} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0170} & \multicolumn{1}{c}{--.0153} & \multicolumn{1}{c}{--.0172} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0233} & \multicolumn{1}{c}{--.0241} & \multicolumn{1}{c}{--.0169} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2481} & \multicolumn{1}{c}{--.1034} & \multicolumn{1}{c}{--.0728} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.3174} & \multicolumn{1}{c}{--.1303} & \multicolumn{1}{c}{--.0812} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1555} & \multicolumn{1}{c}{--.0741} & \multicolumn{1}{c}{--.0589} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1568} & \multicolumn{1}{c}{--.0730} & \multicolumn{1}{c}{--.0565} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.3114} & \multicolumn{1}{c}{--.1513} & \multicolumn{1}{c}{--.0852} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6020} & \multicolumn{1}{c}{--.4844} & \multicolumn{1}{c}{--.8613} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.8997} & \multicolumn{1}{c}{--.7259} & \multicolumn{1}{c}{--.9349} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3103} & \multicolumn{1}{c}{--.2831} & \multicolumn{1}{c}{--.3702} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2994} & \multicolumn{1}{c}{--.2702} & \multicolumn{1}{c}{--.3705} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6726} & \multicolumn{1}{c}{--.6482} & \multicolumn{1}{c}{--.6213} \\
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean.}
\end{tablenotes}
\end{threeparttable}
\end{table}



\clearpage


```{r MULT MNAR 11 Variables, include=FALSE}

mult.mnar.11var.anes <- read.csv("data/anes/mnar/results/anes.mnar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.11var.cces <- read.csv("data/cces/mnar/results/cces.mnar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.11var.frame <- read.csv("data/framing/mnar/results/framing.mnar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mnar.11var.anes$diff[mult.mnar.11var.anes$method == "true"] <- mult.mnar.11var.anes$value[mult.mnar.11var.anes$method == "true"]
mult.mnar.11var.cces$diff[mult.mnar.11var.cces$method == "true"] <- mult.mnar.11var.cces$value[mult.mnar.11var.cces$method == "true"]
mult.mnar.11var.frame$diff[mult.mnar.11var.frame$method == "true"] <- mult.mnar.11var.frame$value[mult.mnar.11var.frame$method == "true"]

levels(mult.mnar.11var.anes$method) <- levels(mult.mnar.11var.cces$method) <- levels(mult.mnar.11var.frame$method) <-
  levs


mult.un.meth <- mult.mnar.11var.anes$method %>% unique
mult.un.meth.len <- mult.un.meth %>% length
mult.un.vars <- c(mult.mnar.11var.anes$variable %>% as.character,
                  mult.mnar.11var.cces$variable %>% as.character,
                  mult.mnar.11var.frame$variable %>% as.character) %>%
  unique
mult.un.vars.len <- mult.un.vars %>% length
mult.un.anes.len <- mult.mnar.11var.anes$variable %>% unique %>% length
mult.un.cces.var <- mult.mnar.11var.cces$variable %>% unique %>% as.character
mult.un.cces.len <- mult.un.cces.var %>% length
mult.un.frame.var <- mult.mnar.11var.frame$variable %>% unique %>% as.character
mult.un.frame.len <- mult.un.frame.var %>% length

mult.variable <- rep(mult.un.vars, each = mult.un.meth.len)
mult.method <- rep(mult.un.meth, mult.un.vars.len) %>% as.character
mult.meth.len <- mult.method %>% length

mult.mnar.11var <- cbind(mult.method, mult.variable) %>% as.data.frame

mult.mnar.11var$mult.anes.col <- c(mult.mnar.11var.anes$diff,
                                  rep("---",
                                      mult.un.meth.len * (mult.un.vars.len - mult.un.anes.len)))
mult.mnar.11var$mult.cces.col <- rep("---", mult.meth.len) %>% as.character
mult.mnar.11var$mult.frame.col <- rep("---", mult.meth.len) %>% as.character

for(i in 1:(mult.un.cces.len)){
  mult.mnar.11var$mult.cces.col[mult.mnar.11var$mult.variable == mult.un.cces.var[i]] <- mult.mnar.11var.cces$diff[mult.mnar.11var.cces$variable == mult.un.cces.var[i]]
  mult.mnar.11var$mult.frame.col[mult.mnar.11var$mult.variable == mult.un.frame.var[i]] <- mult.mnar.11var.frame$diff[mult.mnar.11var.frame$variable == mult.un.frame.var[i]]
}

colnames(mult.mnar.11var) <- col.names

# to make the in-text citations shorter
mult.mnar.11.anes <- mult.mnar.11var$ANES
mult.mnar.11.cces <- mult.mnar.11var$CCES
mult.mnar.11.frame <- mult.mnar.11var$Framing
mult.mnar.11.meth <- mult.mnar.11var$Method
mult.mnar.11.varb <- mult.mnar.11var$Variable

stargazer(mult.mnar.11var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 11 Variables with NA",
          label = "mult.mnar.11var")


```


\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 11 Variables with NA} 
  \label{mult.mnar.11var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0048} & \multicolumn{1}{c}{--.0019} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0097} & \multicolumn{1}{c}{--.0097} & \multicolumn{1}{c}{--.0109} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0061} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{--.0061} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{--.0056} & \multicolumn{1}{c}{--.0057} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0060} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{--.0059} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0060} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0088} & \multicolumn{1}{c}{--.0116} & \multicolumn{1}{c}{--.0068} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0841} & \multicolumn{1}{c}{--.0349} & \multicolumn{1}{c}{--.0258} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1142} & \multicolumn{1}{c}{--.0473} & \multicolumn{1}{c}{--.0291} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0540} & \multicolumn{1}{c}{--.0250} & \multicolumn{1}{c}{--.0206} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0549} & \multicolumn{1}{c}{--.0249} & \multicolumn{1}{c}{--.0199} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2112} & \multicolumn{1}{c}{--.0982} & \multicolumn{1}{c}{--.0342} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2124} & \multicolumn{1}{c}{--.1607} & \multicolumn{1}{c}{--.2819} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3329} & \multicolumn{1}{c}{--.2424} & \multicolumn{1}{c}{--.3271} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1194} & \multicolumn{1}{c}{--.1135} & \multicolumn{1}{c}{--.1257} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1141} & \multicolumn{1}{c}{--.1102} & \multicolumn{1}{c}{--.1244} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2978} & \multicolumn{1}{c}{--.0974} & \multicolumn{1}{c}{--.2074} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0036} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0031} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0011} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0066} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0036} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0034} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0022} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{--.0033} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0077} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0046} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0120} & \multicolumn{1}{c}{--.0095} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0035} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0031} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0112} & \multicolumn{1}{c}{--.0088} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0080} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0060} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0028} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0067} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0064} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0056} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0082} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0028} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0037} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0067} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0061} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0055} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0139} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0021} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0021} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0156} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0164} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0110} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0110} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0345} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0138} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0130} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0111} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0105} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0348} \\ 
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize



### Increased Missingness {#ordmiss-results-increaseNA}


```{r Increasing Missingness Percentage, include=FALSE}

mar.5var.frame.20 <- mar.5var.frame
mar.5var.frame.50 <- read.csv("data/framing/mar/results/framing.mar.results.5var.1000n.1000it.50perc.csv") %>% .[,-1] %>% dropZero.addPlus
mar.5var.frame.80 <- read.csv("data/framing/mar/results/framing.mar.results.5var.1000n.1000it.80perc.csv") %>% .[,-1] %>% dropZero.addPlus

mar.5var.frame.20$diff[mar.5var.frame.20$method == "true"] <- 
  mar.5var.frame.50$diff[mar.5var.frame.50$method == "true"] <- 
  mar.5var.frame.80$diff[mar.5var.frame.80$method == "true"] <- 
  mar.5var.frame.20$value[mar.5var.frame.20$method == "true"]

levels(mar.5var.frame.20$method) <- 
  levels(mar.5var.frame.50$method) <- 
  levels(mar.5var.frame.80$method) <- 
  levs

mar.5var.old.frame <- cbind(mar.5var.frame.20[,c(1,2,4)], mar.5var.frame.50[,4], mar.5var.frame.80[,4])
colnames(mar.5var.old.frame) <- c("Method", "Variable", "20% NA", "50% NA", "80% NA")

# to make the in-text citations shorter
frame.NA20 <- mar.5var.old.frame$`20% NA`
frame.NA50 <- mar.5var.old.frame$`50% NA`
frame.NA80 <- mar.5var.old.frame$`80% NA`
frame.80.meth <- mar.5var.old.frame$Method
frame.80.var <- mar.5var.old.frame$Variable

stargazer(mar.5var.old.frame, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods for Increasing Percentages of Missing Data (Framing Experiment Data)",
          label = "mar.5var.old.frame")

```


\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods for Increasing Percentages of Missing Data (Framing Experiment Data)} 
  \label{mar.5var.old.frame} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{20\% NA} & \multicolumn{1}{c}{50\% NA} & \multicolumn{1}{c}{80\% NA} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.4660} & \multicolumn{1}{c}{.4660} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0016} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0008} & \multicolumn{1}{c}{+.0018} & \multicolumn{1}{c}{+.0037} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0004} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{+.0004} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0340} & \multicolumn{1}{c}{--.0841} & \multicolumn{1}{c}{--.1393} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.5260} & \multicolumn{1}{c}{.5260} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0004} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0005} & \multicolumn{1}{c}{+.0009} & \multicolumn{1}{c}{+.0014} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{--.0006} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0256} & \multicolumn{1}{c}{--.0632} & \multicolumn{1}{c}{--.1051} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{3.2170} & \multicolumn{1}{c}{3.2170} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0213} & \multicolumn{1}{c}{--.0604} & \multicolumn{1}{c}{--.0908} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0248} & \multicolumn{1}{c}{--.0679} & \multicolumn{1}{c}{--.1007} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0714} & \multicolumn{1}{c}{--.1833} & \multicolumn{1}{c}{--.3219} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{3.0890} & \multicolumn{1}{c}{3.0890} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0119} & \multicolumn{1}{c}{--.0371} & \multicolumn{1}{c}{--.0594} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0192} & \multicolumn{1}{c}{--.0550} & \multicolumn{1}{c}{--.0805} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0009} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0014} & \multicolumn{1}{c}{+.0028} & \multicolumn{1}{c}{+.0039} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1367} & \multicolumn{1}{c}{--.3076} & \multicolumn{1}{c}{--.4850} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{37.9120} & \multicolumn{1}{c}{37.9120} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3650} & \multicolumn{1}{c}{--1.0406} & \multicolumn{1}{c}{--1.5789} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3923} & \multicolumn{1}{c}{--1.1319} & \multicolumn{1}{c}{--1.6962} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{+.0043} & \multicolumn{1}{c}{--.0005} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{+.0047} & \multicolumn{1}{c}{+.0034} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--1.0641} & \multicolumn{1}{c}{--2.3051} & \multicolumn{1}{c}{--3.4885} \\  
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean.}
\end{tablenotes}
\end{threeparttable}
\end{table}

\clearpage

### Speed {#ordmiss-results-speed}


```{r Runtimes 5/12 Variables MAR, include=FALSE}

run.5var.anes <- read.csv("data/anes/mar/runtimes/anes.mar.runtime.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.5var.cces <- read.csv("data/cces/mar/runtimes/cces.mar.runtime.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.5var.frame <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]

run.12var.anes <- read.csv("data/anes/mar/runtimes/anes.mar.runtime.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.12var.cces <- read.csv("data/cces/mar/runtimes/cces.mar.runtime.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.12var.frame <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]

run.5var.12var <- data.frame(matrix(NA, 4, 7))
colnames(run.5var.12var) <- c("Method", "ANES5", "CCES5", "Framing5", "ANES12", "CCES12", "Framing12")
run.5var.12var$Method <- run.5var.anes$V2

runs <- list(run.5var.anes, run.5var.cces, run.5var.frame,
             run.12var.anes, run.12var.cces, run.12var.frame)

for(x in 1:length(runs)){
  run.5var.12var[1:4, x+1] <- runs[[x]][,2]
}

run.meth <- run.5var.12var$Method

# so I can use how much slower amelia is than hd.ord
hd.am.div <- sapply(2:7, 
                    function(x)
                      run.5var.12var[run.meth == "amelia", x] / 
                      run.5var.12var[run.meth == "hd.ord", x]) 

stargazer(run.5var.12var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          title = "Runtimes of Multiple Imputation Methods (in Minutes) by Number of Imputed Variables",
          label = "runtimes5var12var")


```


\begin{table}[!htbp] \centering 
  \caption{Runtimes of Multiple Imputation Methods (in Minutes) by Number of Imputed Variables} 
  \label{runtimes5var12var} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{5 Variables with NA} & \multicolumn{3}{c}{12 Variables with NA}\\ 
\cline{2-7}  \\[-1.8ex]
 & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\cline{2-4} 
\cline{5-7}  \\[-1.8ex]
\multicolumn{1}{c}{hd.ord} & 2.632 & 2.778 & 2.559 & 2.614 & 2.679 & 2.555 \\ 
\multicolumn{1}{c}{hot.deck} & 2.628 & 2.786 & 2.567 & 2.640 & 2.690 & 2.582 \\ 
\multicolumn{1}{c}{amelia} & 9.052 & 10.611 & 8.079 & 9.038 & 10.345 & 8.109 \\ 
\multicolumn{1}{c}{mice} & 50.445 & 57.205 & 48.436 & 104.143 & 113.390 & 103.953 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}


```{r Runtimes Increased Missingness MAR, results='asis', echo=FALSE}

run.20 <- run.5var.frame
run.50 <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.5var.1000n.1000it.50perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.80 <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.5var.1000n.1000it.80perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]

run.all.perc <- cbind(run.20$V1, run.50$V1, run.80$V1) %>% as.data.frame %>% round(., digits = 2)
run.all.perc$V4 <- run.20$V2 %>% as.character
run.all.perc <- run.all.perc[,c(4, 1:3)]
colnames(run.all.perc) <- c("Method", "20% NA", "50% NA", "80% NA")

stargazer(run.all.perc, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          title = "Runtimes of Multiple Imputation Methods (in Minutes) by Percentage of Missingness (Framing Experiment Data)",
          label = "run.all.perc")
```


\clearpage

\clearpage
















### From Before


```{r Runtimes MI Methods, include=FALSE}

oldframe.runtime <- read.csv("data/framing/framing.runtime.5var.1003n.12500it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
anes.runtime <- read.csv("data/anes/anes.runtime.5var.3223n.2396it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
anes.5lev.runtime <- read.csv("data/anes/5lev/anes.5lev.runtime.5var.3145n.2500it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
oldframe.quadrobs.runtime <- read.csv("data/framing/quadrupleObs/framing.quadrobs.runtime.5var.4012n.1500it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
oldframe.2000it.runtime <- read.csv("data/framing/framing.runtime.5var.1003n.2000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order

runtimes <- data.frame(matrix(NA, 7, 6))
colnames(runtimes) <- c("Method", "OldFraming", "ANES2016", "ANES2016_5lev", "OldFramingQuadrObs", "OldFraming_2000it")
runtimes$Method <- c("hd.ord", "hd.norm", "amelia", "mice", "Observations", "Iterations", "Levels")
runtimes$OldFraming <- c(oldframe.runtime[,2], 1003, 12500, 7)
runtimes$ANES2016 <- c(anes.runtime[,2], 3223, 2396, 16)
runtimes$ANES2016_5lev <- c(anes.5lev.runtime[,2], 3145, 2500, 5)
runtimes$OldFramingQuadrObs <- c(oldframe.quadrobs.runtime[,2], 4012, 1500, 7)
runtimes$OldFraming_2000it <- c(oldframe.2000it.runtime[,2], 1003, 2000, 7)

# to make in-text citations shorter
runFullF <- runtimes$OldFraming
runFullA <- runtimes$ANES2016
runFullA5 <- runtimes$ANES2016_5lev
runFullFQ <- runtimes$OldFramingQuadrObs
runFullF2k <- runtimes$OldFraming_2000it
methFull <- runtimes$Method
stargazer(runtimes, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          title = "Runtimes of Multiple Imputation Methods (in Minutes)",
          label = "runtimes")
```


\begin{table}[!htbp] \centering 
  \caption{Runtimes of Multiple Imputation Methods (in Minutes)} 
  \label{runtimes} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{OldFraming} & \multicolumn{1}{c}{ANES2016} & \multicolumn{1}{c}{ANES2016\_5lev} & \multicolumn{1}{c}{OldFramingQuadrObs} \\ 
\cline{2-2} 
\cline{3-3} 
\cline{4-4}
\cline{5-5}\\[-1.8ex]
\multicolumn{1}{c}{hd.ord} & 34.457 & 32.642 & 32.668 & 31.519 \\ 
\multicolumn{1}{c}{hd.norm} & 34.660 & 32.669 & 32.881 & 31.810 \\ 
\multicolumn{1}{c}{amelia} & 77.956 & 33.051 & 33.691 & 30.035 \\ 
\multicolumn{1}{c}{mice} & 616.023 & 293.722 & 298.919 & 277.021 \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Observations} & 1,003 & 3,223 & 3,145 & 4,012 \\ 
\multicolumn{1}{c}{Iterations} & 12,500 & 2,396 & 2,500 & 1,500 \\ 
\multicolumn{1}{c}{Levels} & 7 & 16 & 5 & 7 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

As can be seen in Table \ref{runtimes}, `hd.ord` and `hot.deck` show virtually identical imputation times for the old framing data (n = 1,003), with `hd.ord` being `r ((runFullF[methFull == "hd.norm"]-runFullF[methFull == "hd.ord"])*60) %>% round(., digits = 0)` seconds faster. `amelia`, however, is `r (runFullF[methFull == "amelia"] / runFullF[methFull == "hd.ord"]) %>% round(., digits = 1)` times slower than `hd.ord`. `mice` is `r (runFullF[methFull == "mice"] / runFullF[methFull == "hd.ord"]) %>% round(., digits = 1)` times slower than `hd.ord`. This is a dramatic speed gain. The ANES (n = 3,223) data show only a reduced speed gain. `mice` is still drastically slower than `hd.ord` (by a magnitude of `r (runFullA[methFull == "mice"] / runFullA[methFull == "hd.ord"]) %>% round(., digits = 1)`), but the speed gain is cut in half. The previous speed gain over `amelia` is no longer observable. `hd.ord` and `amelia` now show virtually identical runtimes (with a difference of `r round((runFullA[methFull == "amelia"] - runFullA[methFull == "hd.ord"]) * 60, digits = 0)` seconds in favor of `hd.ord`). 

Three factors might explain this sudden and surprising increase in the performance of `amelia`: The levels of the ordinal variable in question (`education`), the number of iterations, and the number of observations in a data set. The ANES (n = 3,223) data contain 17 levels of `education`, whereas the old framing data (n = 1,003) contain only 7. However, when run with 5 levels of `education` and otherwise virtually identical data, the method performances remain unchanged (see column "ANES2016_5lev"). This rules out the levels of the ordinal variable. Another explanation could be the number of observations and the corresponding possible number of iterations. A high number of observations reduces the computationally feasible number of iterations that can be performed before even powerful machines with 120 GB RAM are maxed out. The old framing data (n = 1,003) contain 1,003 observations and can be computationally run for 12,500 iterations. The 2016 ANES data (n = 3,223) contain more than triple the observations than the old framing data (n = 1,003) and can only be run for 2,396 iterations. Indeed, when we quadruple the number of observations in the old framing data (n = 4,012) and are thus forced to reduce the number of possible iterations to 1,500, we observe that `amelia` is now the fastest method (see column "OldFramingQuadrObs"). It thus appears that `amelia` is fast with a low number of iterations and slow with a high number of iterations. 

This would lead us to predict that `amelia` should be the fastest method when the old framing data (n = 1,003) is run for a low number of iterations (2,000). That is not the case: `amelia` is `r (runFullF2k[methFull == "amelia"] / runFullF2k[methFull == "hd.ord"]) %>% round(., digits = 1)` times slower than `hd.ord` (see column "OldFraming_2000it"); on the same level as the 12,500-iteration-run of the old framing data (n = 1,003). This means it's not the number of iterations but the number of observations that affects `amelia`'s relative lack of speed compared to `hd.ord`. `amelia` appears to be much slower than `hd.ord` for around 1,000 observations but on equal footing for 3,000+ observations. 



```{r Runtimes MI Methods 1000 Observations 10000 Iterations, include=FALSE}

cces.runtime.1000n.10000it <- read.csv("data/cces/cces.runtime.5var.1000n.10000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
oldframe.runtime.1000n.10000it <- read.csv("data/framing/framing.runtime.5var.1000n.10000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
anes.7lev.runtime.1000n.10000it <- read.csv("data/anes/7lev/anes.7lev.runtime.5var.1000n.10000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order

cces.runtime.1000n.1000it.more.var <- read.csv("data/cces/cces.runtime.16var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
oldframe.runtime.1000n.1000it.more.var <- read.csv("data/framing/framing.runtime.13var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order
anes.7lev.runtime.1000n.1000it.more.var <- read.csv("data/anes/7lev/anes.7lev.runtime.22var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)] # reverse column order


runtimes.1000n <- data.frame(matrix(NA, 8, 7))
colnames(runtimes.1000n) <- c("Method", 
                              "CCES10kIt", "OldFraming10kIt", "ANES10kIt", 
                              "CCES1kIt", "OldFraming1kIt", "ANES1kIt")
runtimes.1000n$Method <- c("hd.ord", "hd.norm", "amelia", "mice", 
                           "Observations", "Iterations", "Ordinal Levels", 
                           "Variables with NAs")

runtimes.1000n$CCES10kIt <- c(cces.runtime.1000n.10000it[,2], 1000, 10000, 6, 5)
runtimes.1000n$OldFraming10kIt <- c(oldframe.runtime.1000n.10000it[,2], 1000, 10000, 7, 5)
runtimes.1000n$ANES10kIt <- c(anes.7lev.runtime.1000n.10000it[,2], 1000, 10000, 7, 5)

runtimes.1000n$CCES1kIt <- c(cces.runtime.1000n.1000it.more.var[,2], 1000, 1000, 6, 16)
runtimes.1000n$OldFraming1kIt <- c(oldframe.runtime.1000n.1000it.more.var[,2], 1000, 1000, 7, 13)
runtimes.1000n$ANES1kIt <- c(anes.7lev.runtime.1000n.1000it.more.var[,2], 1000, 1000, 7, 22)


# to make in-text citations shorter
# run1k10kC <- runtimes.1000n$CCES10kIt
# run1k10kF <- runtimes.1000n$OldFraming10kIt
# run1k10kA <- runtimes.1000n$ANES10kIt
# 
# run1k1kC <- runtimes.1000n$CCES1kIt
# run1k1kF <- runtimes.1000n$OldFraming1kIt
# run1k1kA <- runtimes.1000n$ANES1kIt

meth <- runtimes.1000n$Method

hd.am.div <- sapply(2:7, 
                    function(x)
                      runtimes.1000n[meth == "amelia", x] / 
                      runtimes.1000n[meth == "hd.ord", x]) 

stargazer(runtimes.1000n, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          title = "Runtimes of Multiple Imputation Methods (in Minutes), 1000 Observations",
          label = "runtimes1000n")
```


This is indeed confirmed by Table \ref{runtimes1000n}, where the old framing, the ANES, and the CCES data have all been reduced to 1,000 observations. The left half of the table shows the results for 10,000 iterations and low numbers of variables with NAs (Note: `education` in the ANES data was reduced to 7 levels to make this number of iterations computationally feasible). The right half of the table shows the results for 1,000 iterations and high numbers of variables with NAs. `amelia` is consistently between `r hd.am.div %>% min %>% round(., digits = 1)` and `r hd.am.div %>% max %>% round(., digits = 1)` times slower than `hd.ord` for all three data sets, regardless of the number of iterations and the number of variables with NAs.



\begin{table}[!htbp] \centering 
  \caption{Runtimes of Multiple Imputation Methods (in Minutes), 1000 Observations} 
  \label{runtimes1000n} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{10,000 Iterations} & \multicolumn{3}{c}{1,000 Iterations}\\
\cline{2-7} \\[-1.8ex]
 & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{OldFraming} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{OldFraming} & \multicolumn{1}{c}{ANES} \\ 
\cline{2-4} 
\cline{5-7} \\[-1.8ex]
\multicolumn{1}{c}{hd.ord} & 24.394 & 26.461 & 24.294 & 2.714 & 2.588 & 4.103 \\ 
\multicolumn{1}{c}{hd.norm} & 24.540 & 26.620 & 24.316 & 2.723 & 2.617 & 4.300 \\ 
\multicolumn{1}{c}{amelia} & 57.403 & 68.862 & 50.630 & 7.787 & 6.926 & 8.758 \\ 
\multicolumn{1}{c}{mice} & 449.027 & 527.532 & 390.690 & 158.583 & 116.609 & 336.038 \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Ordinal Levels} & 6 & 7 & 7 & 6 & 7 & 7 \\ 
\multicolumn{1}{c}{Variables with NAs} & 5 & 5 & 5 & 16 & 13 & 22 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table} 



```{r include=FALSE}
# I don't want to risk referring to the wrong table by mistake, so I'm deleting
# the objects for referral after I no longer refer to them
rm(runFullF, runFullA, runFullA5, runFullFQ, runFullF2k, methFull,
   run1k10kF, run1k10kC, run1k10kA, run1k1kC, run1k1kF, run1k1kA,
   meth)
```









## Conclusion {#ordmiss-conclusion}

What doesn't work

-- Increasing percentage of NAs == worse `hd.ord` performance
-- Ordinal and interval variables == worse `hd.ord` performance
-- High number of observations == reduced number of iterations (crashes and/or RAM maxing out)
-- High number of observations == makes `amelia` faster relative to `hd.ord`
-- 17 ANES education levels == increases needed number of iterations
-- 17 ANES education levels == causes `amelia` to stop on CO and Jeff
-- 10,000 iterations == results with 1,000 iterations are just as good
-- `ampute()` with `bycases=FALSE` and `cont=FALSE` == worse `hd.ord` performance, good `na.omit` performance
-- `own.NA()` == `na.omit` performs best (currently in appendix)
-- `own.NA.rows()`== pretty much everything is zero, incl. `na.omit`; `mice` is awful (currently in appendix)
-- Running `hd.ord` with `method = p.draw` == worse `hd.ord` performance
-- Running `hd.ord` with `method = p.draw` == only works with only binary vars in the data
-- Increasing `sdCutoff` == only does something with only binary vars in the data
-- Only binary vars in data == no gain in `hd.ord` performance

`own.NA()` and `own.NA.rows()` resulted in a strong performance of `na.omit`, which should not happen in a missingness mechanism that is supposed to be MAR. The functions thus likely represent a version of MCAR, which puts the usefulness of their imputation results in doubt.




What works

-- Results for binary variables == equal performance of `hd.ord`, `mice`, `amelia`
-- Increasing number of variables with NAs (all, not just binary) == better `hd.ord` performance
-- 1000 observations in data sets == increases `amelia` running time
-- MNAR == MAR in terms of `hd.ord` performance
-- Multiple ordinal variables == same performance as with one ordinal variable

