# QUALITY COMPARISON OF MAJOR MISSING DATA SOLUTIONS FOR DISCRETE DATA WITH A PROPOSED NEW METHOD FOR ORDINAL VARIABLES {#ordmiss}

## Introduction {#ordmiss-intro}

```{r include=FALSE}
# function to make all diff columns absolute values
abs.diff <- function(df){
  df$diff <- df$diff %>% abs
  return(df)
}

# function to drop leading zeroes in numeric columns in data frames (adapted
# from f_num()) and add a plus sign for positive values
dropZero.addPlus <- function (df, digits = 4){
  x <- dplyr::select_if(df, is.numeric)
  for(i in 1:ncol(x)){
    x[,i] <- round(as.numeric(x[,i]), digits)
    x[,i] <- sprintf(paste0("%.", digits, "f"), x[,i])
    x[,i] <- gsub("^0(?=\\.)|(?<=-)0", "", x[,i], perl = TRUE)
  }
  df[, colnames(x)] <- x
  
  for(i in 1:nrow(df)){
    if(grepl("-", df$diff[i]) == FALSE){
      df$diff[i] <- paste0("+", df$diff[i])
    }else{
      df$diff[i] <- paste0("-", df$diff[i])
    }
  }
  return(df)
}

drop.zero <- function (df, digits = 4, p, s, pad.char = NA, ...){
    library(dplyr)
    ldots <- list(...)
    if (length(ldots) > 0) {
        if (!is.null(ldots[["prefix"]]) & missing(p)) 
            p <- ldots[["prefix"]]
        if (!is.null(ldots[["suffix"]]) & missing(s)) 
            s <- ldots[["suffix"]]
    }
    x <- dplyr::select_if(df, is.numeric)
    for(i in 1:ncol(x)){
      x[,i] <- round(as.numeric(x[,i]), digits)
      x[,i] <- sprintf(paste0("%.", digits, "f"), x[,i])
      x[,i] <- gsub("^0(?=\\.)|(?<=-)0", "", x[,i], perl = TRUE)
    }
    df[, colnames(x)] <- x
    return(df)
}

```

Missing data are ubiquitous in survey research [@allison_2002_missing;@raghunathan_2016_missing]. Respondents frequently refuse to answer questions, select "Don't Know" as a response option, or drop out during the response collection process [@honaker_2010_what]. Missing data pose a big problem for researchers because data can typically not be analyzed with statistical software if they contain missing values [@little_2002_statistical;@molenberghs_2007_missing]. 

Scholars have developed several general ways to treat missing data. These range from deleting all observations with missing data (listwise deletion) over randomly drawing a 'similar' respondent to provide a fill-in value for a missing slot (hot decking) to estimating missing values from conditional distributions (multiple imputation) [@rubin_1976_inference;@king_2001_analyzing;@fay_1996_alternative]. 

Listwise deletion has been shown to induce bias with political data [@rees_1997_methods;@reilly_1993_data]. +++ more citations, examples of how widely used listwise deletion is

Hot decking does not reflect statistical uncertainty in the filled-in values since there is only one draw [@kroh_2006_taking;@gill_2013_bayesian]. +++ More detail about the method

Multiple implementation has become the state of the art in missing data management +++ citations, examples, reasons why it's the state of the art

However, multiple imputation is not necessarily always the most suitable method for all types of variables. For non-granular discrete data, for instance, multiple hot deck imputation, a variation over generic multiple imputation, proves more precise [@gill_2012_have]. +++ how does it achieve that

However, multiple hot deck imputation assumes even distances between categories in discrete data. This assumption does not necessarily apply for ordinal variables. I propose a method designed to impute discrete missing data specifically from ordinal variables. Because of the success of multiple hot deck imputation, this method is based on multiple hot deck imputation and adapted to account for the specific circumstances of ordinal variables. Based on the ordered probit model approach in chapter II, it applies a weighted distance solution with newly estimated numeric thresholds from an assumed underlying latent continuous variable to measure the distances between the categories and calculate an affinity score.


This chapter will:

-- Provide theory behind missing data mechanisms, deletion, imputation, multiple imputation
-- Outline `R` packages/functions that implement listwise deletion and variations of multiple imputation, including my proposed new method
  -- `na.omit`
  -- `amelia`
  -- `mice`
  -- `hot.deck`
  -- `hd.ord`
-- Apply these `R` packages to three different sets of survey data
-- Test each package for accuracy and speed for differing types of variables
-- Assess the usefulness of my proposed new method


## Theory {#ordmiss-theory}

### Missing Data Mechanisms {#ordmiss-theory-mechanisms}

MCAR
MAR
NMAR


### Deletion {#ordmiss-theory-delete}

Deletion of incomplete observations, listwise deletion


### Imputation {#ordmiss-theory-impute}

#### Mean {#ordmiss-theory-impute-mean}

Mean is used to substitute values


#### Regression {#ordmiss-theory-impute-regress}

Missing variables for a unit are estimated by predicted values from the regression on the known variables for that unit


#### Hot Decking {#ordmiss-theory-impute-hd}

Recorded units in the sample are used to substitute values

Hot decking (Marker, Juddkins, Winglee (2002), Ernst (198), Kalton and Kish (1981), Ford (1983), David et al. (1986)) (chapter 4, [@little_2002_statistical])
-- by simple random sampling with replacement
-- within adjustment cells
-- nearest neighbor
-- sequential ordered by a covariate

`R` package: +++


### Multiple Imputation {#ordmiss-theory-multimpute}

#### `Amelia` {#ordmiss-theory-multimpute-amelia}

#### `mice` {#ordmiss-theory-multimpute-mice}

#### Multiple Hot Deck Imputation {#ordmiss-theory-multimpute-hdnorm}

`R` package: `hot.deck`

Multiple hot deck imputation (all COPIED OVER from Cranmer, Gill):
-- A non-parametric alternative to multiple imputation
-- A variation of hot deck imputation combined with the repeated imputation and estimation method typical of parametric multiple imputation
-- Designed to work well in situations where (traditional) parametric multiple imputation falls short -- when a discrete variable with a small number of categories has missing values. This can produce nonsensical imputations, biased results and artificially smaller standard errors
-- Maintains the integrity of the data by using draws of actual values from the variable with the missing values to impute missing items
-- Maintains the discrete nature of discrete data and produces more accurate imputations than parametric multiple imputation in a majority of social science applications where the data are discrete
-- Since many political science applications rely on highly discrete measures, multiple hot deck imputation provides the researcher with more accuracy in imputations than parametric multiple imputation, while requiring none of parametric multiple imputation's standard assumptions

Concrete estimation steps:
(1) Create several copies of the dataset.
(2) Search down columns of the data sequentially looking for missing observations
  a) When a missing value is found, compute a vector of affinity scores, for that missing value. This vector is as long as the number of rows in the dataset, minus any rows with missing values for the same variable
  b) Create the imputation cell of best donors for this missing value and draw randomly from it to produce a vector of imputations
  c) Impute one of these values into the appropriate cell of each duplicate dataset for this missing value
(3) Repeat Step 2 until no missing observations remain
(4) Fit the statistic of interest for each dataset
(5) Combine the estimates of the statistic into a single estimate using the combination rules of parametric multiple imputation


#### Ordinal Variable Multiple Hot Deck Imputation {#ordmiss-theory-multimpute-hdord}

Imputation techniques rely on continuous distributional assumptions.
I use my ordered probit estimated latent underlying continuous variable.

Ordinal hot deck imputation: 
-- An extension of multiple hot deck imputation
-- Designed specifically to implement multiple hot deck imputation with ordinal variables
-- Fully utilizes the unevenly spaced yet ordered information provided in ordinal variables
-- A key variable in political science surveys is ordinal: Education. Ordinal hot deck imputation enables researchers to impute missing data using the full information provided in this most important predictor variable

Multiple hot deck imputation uses draws of values from the variable with the missing values (hot decking) to impute them distributionally (multiple imputation) and estimate affinity scores. This score measures how close other respondents are to the one with the missing value. 'Closeness' is measured as the distance between respondents in the variables that do not contain missing values. This is best illustrated with simplified data shown in Table \ref{ordmiss-affscore}.

\begin{table}[ht]
  \centering
  \begin{tabular}{lccccc}
  \bottomrule 
  \midrule
  Respondent & Age & Party ID & Education & Income & Gender\\
  \hline
  A & 25 & Republican & High School Graduate & \$40-50,000 & Male \\
  B & 40 & NA & Some High School &  \$30-40,000 & Female\\
  C & 30 & Democrat & Bachelor's Degree &  \$60-70,000 & Female\\
  \bottomrule 
  \end{tabular}
  \caption{Illustrative Data}
  \label{ordmiss-affscore}
\end{table}

Respondent B shows missing data for party ID. To impute a fill-in value, we look at how close respondents A and C are to B in terms of age, education, income, and gender. C is closer to B in terms of age and they share the same gender. A is closer to B on education and income. Multiple hot deck imputation measures these distances and estimates affinity scores for respondents A and C. B then receives the party ID fill-in value from whichever respondent has the higher score. The algorithm building the affinity score, however, assumes evenly spaced distances between categories. This is the case for age, income, and gender, but not for education, since education is an ordinal variable. Applying multiple hot deck imputation here would misrepresent the data.

`R` functions: `hd.ord`

`education` is crucial to test the performance of `hd.ord`, which was designed specifically for ordinal variables. `hd.ord` in turn depends on another specifically designed function called `OPMOrd`. `OPMOrd` applies `polr` to an ordinal variable (here `education`) to estimate the underlying latent continuous variable. `polr` can only be run on data without missing variables. +++



## Data {#ordmiss-data}

I ampute data for three different sets of survey data: An experiment on moral framing I ran on MTurk in 2017 (original data), data from the 2016 ANES, and data from the 2016 CCES. All data are amputed with the `ampute` function from the `mice` package (+++ some citation that talks about ampute here). Each data set is imputed with five different functions: `amelia`, `mice`, `hd.ord`, `hot.deck`, and `na.omit`.

`amelia` is from the `Amelia` package. `mice` is from the `mice` package. Both are used with their default settings unless specified otherwise. `hot.deck` is from Gill and Cranmer's multiple hot deck imputation package `hot.deck`. `hd.ord` is my ordinal variable adaptation of `hot.deck`. `na.omit` applies list-wise deletion. I test each function for imputation accuracy and speed for binary, ordinal, and nominal variables in all three data sets. Each data set contains two ordinal (`Education`, `Interest`), two nominal (`Age`, `Income`) and numerous binary variables. In order to enable factually accurate comparison and unless specified otherwise, each data set contains 1,000 observations and six levels of the ordinal variable `Education`. 1,000 observations represent a common size for survey experiment data, and the `polr` analysis from section \ref{ordblock-data} estimates five or six levels to best represent `Education` in a US context. Imputation of each data set was carried out with each of the five imputation methods for 1,000 iterations. With the exception of Table \ref{mar.5var.old.frame}, 20 percent NA were randomly amputed in each iteration for each data set.

Sections \ref{ordmiss-results-mar} to \ref{ordmiss-results-increaseNA} show the results in terms of performance accuracy. Since each data set is complete, we know the true variable mean of all variables. This serves as the baseline of comparison for the performance of each imputation method. First, I impute all data sets MAR (section \ref{ordmiss-results-mar}) and MNAR (section \ref{ordmiss-results-mnar}) for five and 12 amputed variables. The five amputed variables are consistent across all three data sets: `Democrat` (binary), `Male` (binary), `Interest` (ordinal, scaled from 1 to 4), `Income` (nominal), and `Age` (nominal). The 12 amputed variables contain additional variables that differ between each data set due to availability in the data. In section \ref{ordmiss-results-increaseOrd}, I then increase the number of ordinal variables to be treated by `polr` for `hd.ord` by including `Interest`. Imputations are also conducted MAR and MNAR for four and 11 amputed variables. The variables are the same as in sections \ref{ordmiss-results-mar} and \ref{ordmiss-results-mnar}, but without including `Interest`. Finally, I increase the amount of missing data to 50 and 80 percent (section \ref{ordmiss-results-increaseNA}).

Section \ref{ordmiss-results-speed} shows the results in terms of performance speed by the number of imputed variables (Table \ref{runtimes5var12var}) and the percentage of missingness (Table \ref{run.all.perc}). All running times were achieved on a Code Ocean AWS EC2 instance with 16 cores and 120 GB of memory.




## Results {#ordmiss-results}

<!--
I didn't find any scenario where hd.ord actually did significantly and consistently better than amelia or mice. It comes close on occasion for some binary variables and MNAR, but not often and consistently enough. I told Jeff this, and he asked me to write the chapter along my findings -- that the assumption behind polr didn't pan out, at least not for missing data. Everything below is built around that argument.

If it should come up, maybe because a committee member is unhappy, who knows, these are half-hearted ideas I currently have that I might possibly still investigate if I had to:
-- Something with correlation. When I made the coding error that resulted in sampling from 85 observations, amelia was awful and hd.ord much better. Jeff also uses very high correlation in his hot.deck paper (I believe it was 0.8). Jeff also used data on modernization theory for 135 countries between 1950 and 1990, though. That data is very different from surveys and doesn't suffer from any external validity problems. I'm not sure this can be applied to surveys. I frame my stuff around surveys, and what good are artificial data with super high correlations that don't occur in the 'wild' in actual surveys?
-- My second idea is related to the first, I suspect: If hd.ord was close or good in my analyses so far, it was for framing. Why? I would guess that it has to do with correlations and external validity. My sample is markedly different from ANES or CCES when you look at the true variable means. The correlations are probably also very different. That would mean that hd.ord works well for non-externally valid samples -- and what good would that be, really?
-->



<!-- ---- MAIN TEXT ---- -->

<!-- MAR  -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- 12 variables: Dem, Male, Interest, Inc, Age, Black, Empl + 5 selected -->

<!-- MNAR -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- 12 variables: Dem, Male, Interest, Inc, Age, Black, Empl + 5 selected -->

<!-- INCREASED ORDINAL VARIABLES (DVs: educ, interest): -->
<!-- MAR -->
<!-- 4 variables: Dem, Male, Inc, Age -->
<!-- 11 variables: Dem, Male, Inc, Age, Black, Empl + 5 selected -->

<!-- MNAR -->
<!-- 4 variables: Dem, Male, Inc, Age -->
<!-- 11 variables: Dem, Male, Inc, Age, Black, Empl + 5 selected -->

<!-- INCREASED MISSINGNESS (MAR, 20, 50, 80 percent): -->
<!-- Framing, 1000 iterations, 5 variables: Dem, Male, Interest, Inc, Age -->

<!-- SPEED: -->
<!-- MAR 5 variables, MAR 12 variables -->
<!-- MAR 20, 50, 80 percent framing -->



<!-- ---- APPENDIX ---- -->

<!-- ALL OBSERVATIONS (section \ref{app-ordmiss-allObs}): -->
<!-- ANES all obs. 1000 iterations, CCES all obs. 10 iterations (maxed out RAM) -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR (Table \ref{mar.5var.all}) and MNAR (\ref{mnar.5var.all}) -->


<!-- INCREASED MISSINGNESS (section \ref{app-ordmiss-increaseNA}): -->
<!-- CCES 10,000 iterations -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR -->
<!-- 20, 50, 80 percent -->


<!-- SPEED (section \ref{app-ordmiss-speed}): -->
<!-- CCES 10,000 iterations -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR -->
<!-- 20, 50, 80 percent -->

<!-- ANES all obs. 1000 iterations, CCES all obs. 10 iterations (maxed out RAM) -->
<!-- 5 variables: Dem, Male, Interest, Inc, Age -->
<!-- MAR -->


<!--
Problem with CCES 1,000 n 10,000 its MAR 5 Var 20, 50, 80 percent (which I had planned for the appendix):
The 20 percent worked fine on CO, but 50 percent failed because RAM was maxed out. 80 percent will then probably fail as well

Problem with CCES 5 Var all obs. (MAR + MNAR) (which I had planned for the appendix):
No more than 10 iterations are possible before RAM is maxed out, on Jeff and CO
-->




### MAR {#ordmiss-results-mar}

```{r Levels Overall, include=FALSE}
levs <- c("amelia", "hot.deck", "hd.ord", "mice", "na.omit", "true")
col.names <- c("Method", "Variable", "ANES", "CCES", "Framing")
```


```{r MAR 5 Variables, include=FALSE}

mar.5var.anes <- read.csv("data/anes/mar/results/anes.mar.results.5var.1000n.1000it.20perc.csv")  %>% .[,-1] %>% dropZero.addPlus
mar.5var.cces <- read.csv("data/cces/mar/results/cces.mar.results.5var.1000n.1000it.20perc.csv")  %>% .[,-1] %>% dropZero.addPlus
mar.5var.frame <- read.csv("data/framing/mar/results/framing.mar.results.5var.1000n.1000it.20perc.csv")  %>% .[,-1] %>% dropZero.addPlus

mar.5var.anes$diff[mar.5var.anes$method == "true"] <- mar.5var.anes$value[mar.5var.anes$method == "true"]
mar.5var.cces$diff[mar.5var.cces$method == "true"] <- mar.5var.cces$value[mar.5var.cces$method == "true"]
mar.5var.frame$diff[mar.5var.frame$method == "true"] <- mar.5var.frame$value[mar.5var.frame$method == "true"]

levels(mar.5var.anes$method) <- levels(mar.5var.cces$method) <- levels(mar.5var.frame$method) <-
  levs

mar.5var <- cbind(mar.5var.anes[, c(1,2,4)], mar.5var.cces[,4], mar.5var.frame[,4])
colnames(mar.5var) <- col.names

# to make the in-text citations shorter
mar.5.anes <- mar.5var$ANES
mar.5.cces <- mar.5var$CCES
mar.5.frame <- mar.5var$Framing
mar.5.meth <- mar.5var$Method
mar.5.var <- mar.5var$Variable

stargazer(mar.5var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MAR, 5 Variables with NA",
          label = "mar.5var")

```

<!--
MAR 5 Var
Explain vars: Dem and Male binary, Interest ordinal (scale 1-4), Inc and Age nominal
	Binary
		hd.ord on par or worse than hot.deck for all three ds for both vars
		mice best overall across all ds and vars
		mice and amelia very close (.0001 difference)
		More difference for ANES (.0003 mice vs .0011 hd.ord Dem, .0001 mice vs. .0013 hd.ord Male) and Male CCES (.0001 amelia vs. .0014 hd.ord)
		Fewer difference for Dem CCES (.0001 amelia vs. .0004 hd.ord)
		hot.deck performs on par with mice and amelia for framing for both vars
		hd.ord further off for framing as well (.0008 vs. .0000 mice Dem; .0005 vs. .0000 amelia Male)
	Ordinal
		hd.ord worst for all three ds, with considerable distance to hot.deck (.0191 vs. .0130 ANES; .0196 vs. .0125 CCES; .0248 vs. .0213 framing)
		mice and amelia by far best across all ds
		Much larger performance difference between methods for ordinal than for binary: mice is not more than .0003 (Dem ANES) away from true value for all ds. hd.ord's max difference is .0248 (framing)
		Equal performance of mice and amelia, with the edge to mice because of CCES (.0000 vs. 0.0003)
	Nominal
		hd.ord worst for all three ds for both vars
		Again considerable distance to hot.deck
		mice best for Inc
		amelia best for Age
		Even larger performance difference between methods: mice is no more than .0014 (framing) away from true value across ds for Inc. hd.ord's max difference is .1278 (ANES)
		Same for amelia: amelia's max difference is .0039 (framing). hd.ord's is .4597 (ANES)
-->

This section shows the imputation results for the MAR missing data mechanism. MAR amputation was achieved by setting the `mech` argument in the `ampute` function to `MAR`. Table \ref{mar.5var} shows the results of imputing all data sets MAR for five amputed variables. For the two binary variables, `Dem` and `Male`, `hd.ord` performs on par or worse than `hot.deck` for all data sets, while `mice` and `amelia` perform best. `hd.ord` is relatively close for CCES `Dem` (`r mar.5.cces[mar.5.meth == "amelia" & mar.5.var == "Dem"]` `amelia` vs. `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Dem"]` `hd.ord`) but further away for ANES ( `r mar.5.anes[mar.5.meth == "mice" & mar.5.var == "Dem"]` `mice` vs. `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Dem"]` `hd.ord` `Dem`; `r mar.5.anes[mar.5.meth == "mice" & mar.5.var == "Male"]` `mice` vs. `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Male"]` `hd.ord` `Male`) and CCES `Male` (`r mar.5.cces[mar.5.meth == "amelia" & mar.5.var == "Male"]` `amelia` vs. `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Male"]` `hd.ord`).

\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. MAR, 5 Variables with NA} 
  \label{mar.5var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0010} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0011} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0008} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0004} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0290} & \multicolumn{1}{c}{--.0229} & \multicolumn{1}{c}{--.0340} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0013} & \multicolumn{1}{c}{--.0011} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0013} & \multicolumn{1}{c}{--.0014} & \multicolumn{1}{c}{+.0005} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0392} & \multicolumn{1}{c}{--.0414} & \multicolumn{1}{c}{--.0256} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0130} & \multicolumn{1}{c}{--.0125} & \multicolumn{1}{c}{--.0213} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0191} & \multicolumn{1}{c}{--.0196} & \multicolumn{1}{c}{--.0248} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0705} & \multicolumn{1}{c}{--.0724} & \multicolumn{1}{c}{--.0714} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1068} & \multicolumn{1}{c}{--.0259} & \multicolumn{1}{c}{--.0119} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1278} & \multicolumn{1}{c}{--.0407} & \multicolumn{1}{c}{--.0192} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0008} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{+.0014} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.5631} & \multicolumn{1}{c}{--.2468} & \multicolumn{1}{c}{--.1367} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3888} & \multicolumn{1}{c}{--.2616} & \multicolumn{1}{c}{--.3650} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.4597} & \multicolumn{1}{c}{--.3895} & \multicolumn{1}{c}{--.3923} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0007} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{--.0039} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0017} & \multicolumn{1}{c}{--.0073} & \multicolumn{1}{c}{--.0049} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--1.1875} & \multicolumn{1}{c}{--1.2361} & \multicolumn{1}{c}{--1.0641} \\
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean, indicated with a + or -- sign.}
\end{tablenotes}
\end{threeparttable}
\end{table} 

For the ordinal variable, `Interest`, `hd.ord` performs worst for all data sets, with considerable distance to `hot.deck` (`r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Interest"]` vs. `r mar.5.anes[mar.5.meth == "hot.deck" & mar.5.var == "Interest"]` ANES; `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Interest"]` vs. `r mar.5.cces[mar.5.meth == "hot.deck" & mar.5.var == "Interest"]` CCES; `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Interest"]` vs. `r mar.5.frame[mar.5.meth == "hot.deck" & mar.5.var == "Interest"]` Framing). `mice` and `amelia` perform by far best across all data sets. The performance differences between the methods are far larger for the ordinal than for the binary variables: `mice` is not more than `r mar.5.anes[mar.5.meth == "mice" & mar.5.var == "Interest"]` (ANES) away from the true value across all data sets, while the maximum difference for `hd.ord` amounts to `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Interest"]` (Framing).

For the nominal variables, `Inc` and `Age`, `hd.ord` also performs worst for all data sets. The distance to `hot.deck` is once more considerable. `mice` performs best for `Inc` and `amelia` shows the best results for `Age`. The performance differences between the methods are even larger here: For `Inc`, `mice` is not more than `r mar.5.frame[mar.5.meth == "mice" & mar.5.var == "Inc"]` (Framing) away from the true value across all data sets, but the maximum difference for `hd.ord` is `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Inc"]` (ANES). Similarly, `amelia`'s largest deviation from the true value for `Age` is `r mar.5.frame[mar.5.meth == "amelia" & mar.5.var == "Age"]` (Framing) as opposed to `hd.ord`'s `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Age"]` (ANES).



```{r MAR 12 Variables, include=FALSE}

mar.12var.anes <- read.csv("data/anes/mar/results/anes.mar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mar.12var.cces <- read.csv("data/cces/mar/results/cces.mar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mar.12var.frame<- read.csv("data/framing/mar/results/framing.mar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mar.12var.anes$diff[mar.12var.anes$method == "true"] <- mar.12var.anes$value[mar.12var.anes$method == "true"]
mar.12var.cces$diff[mar.12var.cces$method == "true"] <- mar.12var.cces$value[mar.12var.cces$method == "true"]
mar.12var.frame$diff[mar.12var.frame$method == "true"] <- mar.12var.frame$value[mar.12var.frame$method == "true"]

levels(mar.12var.anes$method) <- levels(mar.12var.cces$method) <- levels(mar.12var.frame$method) <-
  levs

un.meth <- mar.12var.anes$method %>% unique
un.meth.len <- un.meth %>% length
un.vars <- c(mar.12var.anes$variable %>% as.character,
                 mar.12var.cces$variable %>% as.character, 
                 mar.12var.frame$variable %>% as.character) %>%
  unique
un.vars.len <- un.vars %>% length
un.anes.len <- mar.12var.anes$variable %>% unique %>% length
un.cces.var <- mar.12var.cces$variable %>% unique %>% as.character
un.cces.len <- un.cces.var %>% length
un.frame.var <- mar.12var.frame$variable %>% unique %>% as.character
un.frame.len <- un.frame.var %>% length
Variable <- rep(un.vars, each = un.meth.len)
Method <- rep(un.meth, un.vars.len) %>% as.character
meth.len <- Method %>% length

mar.12var <- cbind(Method, Variable) %>% as.data.frame

mar.12var$mar.anes.col <- c(mar.12var.anes$diff, 
                            rep("---", 
                                un.meth.len * (un.vars.len - un.anes.len)))
mar.12var$mar.cces.col <- rep("---", meth.len) %>% as.character
mar.12var$mar.frame.col <- rep("---", meth.len) %>% as.character

for(i in 1:(un.cces.len)){
  mar.12var$mar.cces.col[mar.12var$Variable == un.cces.var[i]] <- mar.12var.cces$diff[mar.12var.cces$variable == un.cces.var[i]]
  mar.12var$mar.frame.col[mar.12var$Variable == un.frame.var[i]] <- mar.12var.frame$diff[mar.12var.frame$variable == un.frame.var[i]]
}

colnames(mar.12var) <- col.names

# to make the in-text citations shorter
mar.12.anes <- mar.12var$ANES
mar.12.cces <- mar.12var$CCES
mar.12.frame <- mar.12var$Framing
mar.12.meth <- mar.12var$Method
mar.12.var <- mar.12var$Variable

stargazer(mar.12var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MAR, 12 Variables with NA",
          label = "mar.12var")

```

<!--
MAR 12 Var
Explain vars: First 5 vars the same as for MAR 5 Var. Black, Empl, Religious, Married, OwnHome, Rally, Donate, Gay, StudLoans, Hisp, Official, Stud binary. Media and Participation ordinal (1-5). 
	Binary
		Similar picture to MAR 5 Var, though overall hd.ord arguably closer. Max difference now .0006 (Empl ANES and framing)
		amelia and mice best again, often actually zero difference to true value
	Ordinal
		Same picture as before: hd.ord is worst across all ds for all vars (including Media and Participation framing)
		mice and amelia again by far best
		hd.ord less worse than for MAR 5 Var in terms of performance differences. hd.ord's max diff for Interest is now .0106 (framing) (compared to .0248 (framing) for 5 Var). Possibly explained by thinner spread of NAs, so fewer NAs per variable. Media and Participation framing results confirm those for Interest across all ds
	Nominal
		Same picture as before: hd.ord is worst across all ds
		Difference to hot.deck still there but less pronounced than for MAR 5 Var
		mice overall better than amelia for Inc, though .0007 vs. .0013 ANES for amelia
		mice also overall better than amelia for Age, though .0015 vs. .0050 CCES for amelia
		As for ordinal, hd.ord less worse than for MAR 5 Var in terms of performance differences but consistent
-->

Table \ref{mar.12var} shows the results of imputing all data sets MAR for 12 amputed variables. The first five listed variables are the same as for the MAR analysis for five amputed variables in Table \ref{mar.5var}. The remaining variables were chosen based on availability in each data set. As much as possible, the same variables were selected across all data sets. `Black`, `Empl`, `Religious`, `Married`, `OwnHome`, `Rally`, `Donate`, `Gay`, `StudLoans`, `Hisp`, `Official`, and `Stud` are binary variables. `Black` indicates whether a respondent is of African-American origin, `Empl` whether she is currently employed, `Religious` whether she follows a religious belief, `Married` whether she is currently married, `OwnHome` whether she owns her home, `Rally` whether she has attended a political rally, `Donate` whether she has donated to a political candidate, `Gay` whether she identifies as homosexual, `StudLoans` whether she currently has student loans, `Hisp` whether she is of Hispanic origin, `Official` whether she has contacted her political representative, and `Stud` whether she currently is a student. `Media` is an ordinal variable and indicates how much she follows public affairs in the media (scaled from 1 to 5). `Participation` is a nominal variable and shows the accumulative count of political activities she has participated in (scaled from 0 to 4).

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. MAR, 12 Variables with NA} 
  \label{mar.12var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0004} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0191} & \multicolumn{1}{c}{--.0172} & \multicolumn{1}{c}{--.0280} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0256} & \multicolumn{1}{c}{--.0364} & \multicolumn{1}{c}{--.0154} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0095} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0077} & \multicolumn{1}{c}{--.0067} & \multicolumn{1}{c}{--.0106} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0620} & \multicolumn{1}{c}{--.0515} & \multicolumn{1}{c}{--.0721} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0470} & \multicolumn{1}{c}{--.0130} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0591} & \multicolumn{1}{c}{--.0212} & \multicolumn{1}{c}{--.0089} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0007} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0013} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.6303} & \multicolumn{1}{c}{--.2860} & \multicolumn{1}{c}{--.0960} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1391} & \multicolumn{1}{c}{--.0883} & \multicolumn{1}{c}{--.1494} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1835} & \multicolumn{1}{c}{--.1435} & \multicolumn{1}{c}{--.1592} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0056} & \multicolumn{1}{c}{--.0015} & \multicolumn{1}{c}{--.0041} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0048} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0029} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.8638} & \multicolumn{1}{c}{--.5974} & \multicolumn{1}{c}{--.6434} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0092} & \multicolumn{1}{c}{--.0090} & \multicolumn{1}{c}{--.0110} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0006} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0007} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0006} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0006} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0087} & \multicolumn{1}{c}{--.0301} & \multicolumn{1}{c}{--.0157} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0006} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0166} & \multicolumn{1}{c}{--.0234} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0384} & \multicolumn{1}{c}{--.0326} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0334} & \multicolumn{1}{c}{--.0304} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0191} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0320} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0112} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0117} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0072} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0385} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0049} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0984} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0021} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.1003} \\ 
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize

The results are consistent with those presented in Table \ref{mar.5var}. For the binary variables, `amelia` and `mice` again perform best with results actually matching the true variable values, though `hd.ord` arguably shows closer results than in Table \ref{mar.5var} with a maximum difference to a true value of `r mar.12.anes[mar.12.meth == "hd.ord" & mar.12.var == "Empl"]` (ANES and Framing `Empl`). For the ordinal variable, `hd.ord` continues to perform worst across all data sets. The same applies to Framing `Media`. `mice` and `amelia` again show the best results. Note, however, that `hd.ord` is less worse in terms of performance differences when compared to the MAR analysis of five imputed variables. The maximum difference to the true `Interest` value is `r mar.12.frame[mar.12.meth == "hd.ord" & mar.12.var == "Interest"]` (Framing) for 12 variables but `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Interest"]` (Framing) for five variables. This is possibly explained by a thinner spread of missing values across a higher number of variables, resulting in a lower number of NAs in each amputed variable. 

The results for the nominal variables follow the same pattern. `hd.ord` displays the worst results for all data sets. The difference to `hot.deck` is still present though less pronounced than in the MAR analysis of five imputed variables. `mice` overall performs better than `amelia` for `Inc` and `Age`, with the exceptions of ANES `Inc` (`r mar.12.anes[mar.12.meth == "amelia" & mar.12.var == "Inc"]` vs. `r mar.12.anes[mar.12.meth == "mice" & mar.12.var == "Inc"]`) and CCES `Age` (`r mar.12.cces[mar.12.meth == "amelia" & mar.12.var == "Age"]` vs. `r mar.12.cces[mar.12.meth == "mice" & mar.12.var == "Age"]`). The results for Framing `Participation` confirm those for `Inc` and `Age`.




### MNAR {#ordmiss-results-mnar}

```{r MNAR 5 Variables, include=FALSE}

mnar.5var.anes <- read.csv("data/anes/mnar/results/anes.mnar.results.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.5var.cces <- read.csv("data/cces/mnar/results/cces.mnar.results.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.5var.frame <- read.csv("data/framing/mnar/results/framing.mnar.results.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mnar.5var.anes$diff[mnar.5var.anes$method == "true"] <- mnar.5var.anes$value[mnar.5var.anes$method == "true"]
mnar.5var.cces$diff[mnar.5var.cces$method == "true"] <- mnar.5var.cces$value[mnar.5var.cces$method == "true"]
mnar.5var.frame$diff[mnar.5var.frame$method == "true"] <- mnar.5var.frame$value[mnar.5var.frame$method == "true"]

levels(mnar.5var.anes$method) <- levels(mnar.5var.cces$method) <- levels(mnar.5var.frame$method) <-
  levs

mnar.5var <- cbind(mnar.5var.anes[,c(1,2,4)], mnar.5var.cces[,4], mnar.5var.frame[,4])
colnames(mnar.5var) <- col.names

# to make the in-text citations shorter
mnar.5.anes <- mnar.5var$ANES
mnar.5.cces <- mnar.5var$CCES
mnar.5.frame <- mnar.5var$Framing
mnar.5.meth <- mnar.5var$Method
mnar.5.var <- mnar.5var$Variable

stargazer(mnar.5var,
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MNAR, 5 Variables with NA",
          label = "mnar.5var")


```

<!--
MNAR 5 VAR
Vars the same as for MAR 5 Var
	Binary
		Overall difference to true value much higher for all methods for all ds for all vars. Around .0100 for Dem ANES and CCES, around .004 for Dem framing. Around .0125 for Male across all ds. For comparison: Around .0005 for Dem and Male for all ds for MAR 5 Var.
		hd.ord is closer to amelia and mice than for MAR, sometimes more (.0133 hd.ord vs. .0132 amelia Male ANES), sometimes less (.0120 hd.ord vs. .0099 mice Dem ANES). hd.ord actually best of all methods for framing for both vars, but overall amelia and mice perform better
		Interesting: na.omit as good as amelia and mice for Male framing and rather close for the other vars and ds too
	Ordinal
		Consistent picture of overall much higher difference to true value. In terms of method performance, same picture as for MAR: hd.ord worst across all ds. 
		amelia and mice best by far, virtually identical, though with much higher differences than for MAR
		Interesting: na.omit close to hd.ord for framing. 
	Nominal
		Much higher differences to true value, as consistent for all MNAR results. Same picture in terms of method performance, similar to Ordinal
		Interesting: na.omit better than hd.ord for Age ANES. na.omit also better than hd.ord and hot.deck for Age framing
-->

This section shows the imputation results for the MNAR missing data mechanism. MNAR amputation was achieved by setting the `mech` argument in the `ampute` function to `MNAR`. All MAR and MNAR analyses are otherwise identical. Table \ref{mnar.5var} shows the results of imputing all data sets MNAR for five amputed variables. It is immediately noticable that the differences between the methods' imputation results and the true values is much higher for all methods for all variables for all data sets. The results for `Dem`, for instance, hover around .0100 for ANES/CCES and around .004 for Framing, while the `Male` numbers center around .0125 across all data sets. In the corresponding MAR analysis, however, the results for `Dem` and `Male` revealed around .0005 for all data sets. 

\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. MNAR, 5 Variables with NA} 
  \label{mnar.5var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0114} & \multicolumn{1}{c}{--.0099} & \multicolumn{1}{c}{--.0038} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0120} & \multicolumn{1}{c}{--.0105} & \multicolumn{1}{c}{--.0033} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0106} & \multicolumn{1}{c}{--.0102} & \multicolumn{1}{c}{--.0046} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0099} & \multicolumn{1}{c}{--.0101} & \multicolumn{1}{c}{--.0036} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0176} & \multicolumn{1}{c}{--.0140} & \multicolumn{1}{c}{--.0185} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0136} & \multicolumn{1}{c}{--.0116} & \multicolumn{1}{c}{--.0127} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0133} & \multicolumn{1}{c}{--.0124} & \multicolumn{1}{c}{--.0125} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0132} & \multicolumn{1}{c}{--.0121} & \multicolumn{1}{c}{--.0133} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0132} & \multicolumn{1}{c}{--.0120} & \multicolumn{1}{c}{--.0135} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0214} & \multicolumn{1}{c}{--.0219} & \multicolumn{1}{c}{--.0133} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0288} & \multicolumn{1}{c}{--.0246} & \multicolumn{1}{c}{--.0333} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0335} & \multicolumn{1}{c}{--.0296} & \multicolumn{1}{c}{--.0369} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0167} & \multicolumn{1}{c}{--.0146} & \multicolumn{1}{c}{--.0133} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0167} & \multicolumn{1}{c}{--.0146} & \multicolumn{1}{c}{--.0135} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0379} & \multicolumn{1}{c}{--.0372} & \multicolumn{1}{c}{--.0379} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2299} & \multicolumn{1}{c}{--.0928} & \multicolumn{1}{c}{--.0591} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2554} & \multicolumn{1}{c}{--.1038} & \multicolumn{1}{c}{--.0648} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1225} & \multicolumn{1}{c}{--.0578} & \multicolumn{1}{c}{--.0463} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1229} & \multicolumn{1}{c}{--.0566} & \multicolumn{1}{c}{--.0445} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2770} & \multicolumn{1}{c}{--.1334} & \multicolumn{1}{c}{--.0740} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6319} & \multicolumn{1}{c}{--.4596} & \multicolumn{1}{c}{--.7147} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.7415} & \multicolumn{1}{c}{--.5929} & \multicolumn{1}{c}{--.7477} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2450} & \multicolumn{1}{c}{--.2266} & \multicolumn{1}{c}{--.2875} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2369} & \multicolumn{1}{c}{--.2160} & \multicolumn{1}{c}{--.2888} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6427} & \multicolumn{1}{c}{--.6392} & \multicolumn{1}{c}{--.5853} \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean, indicated with a + or -- sign.}
\end{tablenotes}
\end{threeparttable}
\end{table}


For the binary variables, `hd.ord` performs more closely on par with `amelia` and `mice` than in the corresponding MAR analysis above, sometimes more (`r mnar.5.anes[mnar.5.meth == "hd.ord" & mnar.5.var == "Male"]` `hd.ord` vs. `r mnar.5.anes[mnar.5.meth == "amelia" & mnar.5.var == "Male"]` `amelia` ANES `Male`) and sometimes less so (`r mnar.5.anes[mnar.5.meth == "hd.ord" & mnar.5.var == "Dem"]` `hd.ord` vs. `r mnar.5.anes[mnar.5.meth == "mice" & mnar.5.var == "Dem"]` `mice` ANES `Dem`). In addition, `hd.ord` actually represents the best method for both binary variables in the Framing data. Note the interesting results for `na.omit` here: It performs as well as `amelia` and `mice` for Framing `Male`.

The results for the ordinal variables confirm those of the MAR analysis: `hd.ord` represents the worst method across all data sets. `amelia` and `mice` show by far the best results and are virtually identical with each other, though the differences to the true values are much higher than in the MAR analysis -- as is the case for the entire MNAR analysis. `na.omit` shows results that are close to `hd.ord`'s for Framing.

The results for the nominal variables paint the same picture as the ordinal ones. `hd.ord` shows the worst performance. Note that `na.omit` now actually outperforms `hot.deck` for Framing `Age` and `hd.ord` for Framing and ANES `Age`.


```{r MNAR 12 Variables, include=FALSE}

mnar.12var.anes <- read.csv("data/anes/mnar/results/anes.mnar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.12var.cces <- read.csv("data/cces/mnar/results/cces.mnar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mnar.12var.frame <- read.csv("data/framing/mnar/results/framing.mnar.results.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mnar.12var.anes$diff[mnar.12var.anes$method == "true"] <- mnar.12var.anes$value[mnar.12var.anes$method == "true"]
mnar.12var.cces$diff[mnar.12var.cces$method == "true"] <- mnar.12var.cces$value[mnar.12var.cces$method == "true"]
mnar.12var.frame$diff[mnar.12var.frame$method == "true"] <- mnar.12var.frame$value[mnar.12var.frame$method == "true"]

levels(mnar.12var.anes$method) <- levels(mnar.12var.cces$method) <- levels(mnar.12var.frame$method) <-
  levs

# there are several in-between code steps that are identical to MAR 12 Variables
# above, so I didn't include them here

mnar.12var <- cbind(Method, Variable) %>% as.data.frame

mnar.12var$mnar.anes.col <- c(mnar.12var.anes$diff,
                              rep("---",
                                  un.meth.len * (un.vars.len - un.anes.len)))
mnar.12var$mnar.cces.col <- rep("---", meth.len) %>% as.character
mnar.12var$mnar.frame.col <- rep("---", meth.len) %>% as.character

for(i in 1:(un.cces.len)){
  mnar.12var$mnar.cces.col[mnar.12var$Variable == un.cces.var[i]] <- mnar.12var.cces$diff[mnar.12var.cces$variable == un.cces.var[i]]
  mnar.12var$mnar.frame.col[mnar.12var$Variable == un.frame.var[i]] <- mnar.12var.frame$diff[mnar.12var.frame$variable == un.frame.var[i]]
}

colnames(mnar.12var) <- col.names

# to make the in-text citations shorter
mnar.12.anes <- mnar.12var$ANES
mnar.12.cces <- mnar.12var$CCES
mnar.12.frame <- mnar.12var$Framing
mnar.12.meth <- mnar.12var$Method
mnar.12.var <- mnar.12var$Variable

stargazer(mnar.12var,
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. MNAR, 12 Variables with NA",
          label = "mnar.12var")


```

<!--
MNAR 12 VAR
Vars the same as for MNAR 5 Var
	Binary
		Similar picture to MNAR 5 Var. amelia and mice perform better, but often not by much. Occasionally, hd.ord eclipses them (.0013 hd.ord vs. .0014 mice Dem framing; 0.0053 hd.ord vs. .0055 mice and amelia Male ANES).
		na.omit again often performs close to the other methods 
	Ordinal
		Exactly the same as for MNAR 5 Var. hd.ord worst across all ds. mice and amelia far better and virtually identical (including Media and Participation framing).
		na.omit further off than for MNAR 5 Var
	Nominal
		Same method performance as for MNAR 5 Var.
		na.omit better than hot.deck and hd.ord for Age framing (.2239 vs. .2811 and .2989) and Age CCES (.1367 vs. .1732 and .2251)
-->

Table \ref{mnar.12var} shows the results of imputing all data sets MNAR for 12 amputed variables. The results are consistent with those obtained for five amputed variables MNAR. `amelia` and `mice` perform better than `hd.ord` for the binary variables overall, but often not by much. Occasionally, `hd.ord` eclipses them (`r mnar.12.frame[mnar.12.meth == "hd.ord" & mnar.12.var == "Dem"]` vs. `r mnar.12.frame[mnar.12.meth == "mice" & mnar.12.var == "Dem"]` `mice` Framing `Dem`; `r mnar.12.anes[mnar.12.meth == "hd.ord" & mnar.12.var == "Male"]` vs. `r mnar.12.anes[mnar.12.meth == "mice" & mnar.12.var == "Male"]` `mice` and `amelia` ANES `Male`). `na.omit` once more performs close to the other methods.

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. MNAR, 12 Variables with NA} 
  \label{mnar.12var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0046} & \multicolumn{1}{c}{--.0015} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0013} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0018} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0014} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0092} & \multicolumn{1}{c}{--.0081} & \multicolumn{1}{c}{--.0106} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0052} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0051} & \multicolumn{1}{c}{--.0051} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0055} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0093} & \multicolumn{1}{c}{--.0119} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{2.9340} & \multicolumn{1}{c}{3.3290} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0113} & \multicolumn{1}{c}{--.0090} & \multicolumn{1}{c}{--.0139} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0134} & \multicolumn{1}{c}{--.0113} & \multicolumn{1}{c}{--.0150} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0068} & \multicolumn{1}{c}{--.0061} & \multicolumn{1}{c}{--.0053} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0068} & \multicolumn{1}{c}{--.0061} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0236} & \multicolumn{1}{c}{--.0161} & \multicolumn{1}{c}{--.0252} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0899} & \multicolumn{1}{c}{--.0350} & \multicolumn{1}{c}{--.0239} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1046} & \multicolumn{1}{c}{--.0421} & \multicolumn{1}{c}{--.0262} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0495} & \multicolumn{1}{c}{--.0223} & \multicolumn{1}{c}{--.0184} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0503} & \multicolumn{1}{c}{--.0218} & \multicolumn{1}{c}{--.0177} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2088} & \multicolumn{1}{c}{--.0970} & \multicolumn{1}{c}{--.0333} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2571} & \multicolumn{1}{c}{--.1732} & \multicolumn{1}{c}{--.2811} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3081} & \multicolumn{1}{c}{--.2251} & \multicolumn{1}{c}{--.2989} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1100} & \multicolumn{1}{c}{--.1014} & \multicolumn{1}{c}{--.1159} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1047} & \multicolumn{1}{c}{--.0986} & \multicolumn{1}{c}{--.1159} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3397} & \multicolumn{1}{c}{--.1367} & \multicolumn{1}{c}{--.2239} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0035} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{--.0028} \\
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{--.0029} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0011} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0034} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{--.0010} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0052} & \multicolumn{1}{c}{--.0045} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0034} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0031} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0031} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0014} & \multicolumn{1}{c}{--.0111} & \multicolumn{1}{c}{--.0037} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} \\
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0073} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0038} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{--.0096} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0028} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0111} & \multicolumn{1}{c}{--.0090} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0077} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0051} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0048} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0024} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0024} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0035} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0051} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0070} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0011} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0010} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0033} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0049} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0048} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0142} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0023} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0020} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0017} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0142} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0152} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0101} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0101} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0363} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0115} \\
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0115} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0099} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0094} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0358} \\ 
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize

For the ordinal variable, `hd.ord` shows the worst performance across all data sets. `mice` and `amelia` perform far better and display virtually identical result. This also applies to Framing `Media`. `na.omit` does not perform as well as in the corresponding MAR analysis. `mice` and `amelia`'s superior performance is also visible in the results for the ordinal variables, including Framing `Participation`. `na.omit` performs better than `hot.deck` and `hd.ord` for Framing `Age` (`r mnar.12.frame[mnar.12.meth == "na.omit" & mnar.12.var == "Age"]` vs. `r mnar.12.frame[mnar.12.meth == "hot.deck" & mnar.12.var == "Age"]` and `r mnar.12.frame[mnar.12.meth == "hd.ord" & mnar.12.var == "Age"]`), and CCES `Age` (`r mnar.12.cces[mnar.12.meth == "na.omit" & mnar.12.var == "Age"]` vs. `r mnar.12.cces[mnar.12.meth == "hot.deck" & mnar.12.var == "Age"]` and `r mnar.12.cces[mnar.12.meth == "hd.ord" & mnar.12.var == "Age"]`). 




### Increased Number of Ordinal Variables {#ordmiss-results-increaseOrd}

```{r MULT MAR 4 Variables, include=FALSE}

mult.mar.4var.anes <- read.csv("data/anes/mar/results/anes.mar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.4var.cces <- read.csv("data/cces/mar/results/cces.mar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.4var.frame <- read.csv("data/framing/mar/results/framing.mar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mar.4var.anes$diff[mult.mar.4var.anes$method == "true"] <- mult.mar.4var.anes$value[mult.mar.4var.anes$method == "true"]
mult.mar.4var.cces$diff[mult.mar.4var.cces$method == "true"] <- mult.mar.4var.cces$value[mult.mar.4var.cces$method == "true"]
mult.mar.4var.frame$diff[mult.mar.4var.frame$method == "true"] <- mult.mar.4var.frame$value[mult.mar.4var.frame$method == "true"]

levels(mult.mar.4var.anes$method) <- levels(mult.mar.4var.cces$method) <- levels(mult.mar.4var.frame$method) <-
  levs

mult.mar.4var <- cbind(mult.mar.4var.anes[, c(1,2,4)], mult.mar.4var.cces[,4], mult.mar.4var.frame[,4])
colnames(mult.mar.4var) <- col.names

# to make the in-text citations shorter
mult.mar.4.anes <- mult.mar.4var$ANES
mult.mar.4.cces <- mult.mar.4var$CCES
mult.mar.4.frame <- mult.mar.4var$Framing
mult.mar.4.meth <- mult.mar.4var$Method
mult.mar.4.var <- mult.mar.4var$Variable

stargazer(mult.mar.4var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 4 Variables with NA",
          label = "mult.mar.4var")

```

<!--
Increased Ordinal
Treats Education and Interest with polr
Also split into MAR/MNAR and 4/11 Variables
MAR 4 Var
Vars the same as for MAR and MNAR 5 Var, just without Interest (so no ordinal vars here)
	Binary
		hd.ord worst for Dem across all ds. hd.ord better than hot.deck for Male across all ds.
		amelia and mice best, virtually identical, often zero
		Results for hd.ord get slightly worse when compared to MAR 5 Var:
		MAR 5 Var hd.ord: Dem .0011, .0004, .0008. Male .0013, .0014, .0005
		MAR 4 Var hd.ord: Dem .0018, .0005, .0012. Male .0015, .0018, .0011		
	Nominal
		hd.ord worst for all ds for all vars
		amelia and mice far best. mice does better for Inc and Age CCES, amelia does better for Inc and Age framing. Both equally good for Inc and Age ANES
		Consistent with the binary changes from one to two ordinal variables, the results for hd.ord get slightly worse when compared to MAR 5 Var:
		MAR 5 Var hd.ord: Inc .1278, .0407, .0192. Age .4597, .3895, .3923
		MAR 4 Var hd.ord: Inc .1523, .0516, .0225. Age .5431, .4664, .4583
-->

This section shows the imputation results where I increase the number of ordinal variables to be treated by `polr` for `hd.ord`. Specifically, I include `Interest` in the `polr` treatment. The intuition behind this is a strengthening of the underlying latent continuous variable assumption. The results so far do not show superior performance by `hd.ord`. However, this might be due to a lack of 'influence' so far. Perhaps one ordinal variable treated with `polr` is not enough to manifest itself in improved results. By including another ordinal variable in the treatment, this 'influence' is strengthened and the `polr` assumption is put to another test. As in sections \ref{ordmiss-results-mar} and \ref{ordmiss-results-mnar}, imputations are conducted MAR and MNAR. Because `Interest` is moved to the `polr` treatment, the number of imputed variables is reduced to four and 11, respectively, to ensure accurate comparison. This means the amputed variables do not include an ordinal variable any more, since no suitable replacement could be found in the ANES and CCES data. The remaining variables are the same as before.

Table \ref{mult.mar.4var} shows the results of imputing all data sets with two `polr`-treated variables MAR for four amputed variables. `hd.ord` displays the worst results for `Dem` across all data sets and beats only `hot.deck` for `Male`. `amelia` and `mice` perform best and show virtually identically results that often match the true variable means. Comparison with the MAR analysis of five imputed variables reveals that `hd.ord` consistently performs slightly worse here: `r mult.mar.4.anes[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Dem"]`, `r mult.mar.4.cces[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Dem"]`, `r mult.mar.4.frame[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Dem"]` vs. `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Dem"]`, `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Dem"]`, `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Dem"]` for `Dem` and `r mult.mar.4.anes[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Male"]`, `r mult.mar.4.cces[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Male"]`, `r mult.mar.4.frame[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Male"]` vs. `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Male"]`, `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Male"]`, `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Male"]` for `Male`.

\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 4 Variables with NA} 
  \label{mult.mar.4var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0008} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0005} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0018} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{+.0012} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0333} & \multicolumn{1}{c}{--.0294} & \multicolumn{1}{c}{--.0357} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0022} & \multicolumn{1}{c}{--.0019} & \multicolumn{1}{c}{+.0015} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0015} & \multicolumn{1}{c}{--.0018} & \multicolumn{1}{c}{+.0011} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0396} & \multicolumn{1}{c}{--.0407} & \multicolumn{1}{c}{--.0297} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0830} & \multicolumn{1}{c}{--.0246} & \multicolumn{1}{c}{--.0093} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1523} & \multicolumn{1}{c}{--.0516} & \multicolumn{1}{c}{--.0225} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0010} & \multicolumn{1}{c}{--.0006} & \multicolumn{1}{c}{+.0009} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0008} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{+.0020} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.5771} & \multicolumn{1}{c}{--.2564} & \multicolumn{1}{c}{--.1400} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2889} & \multicolumn{1}{c}{--.2350} & \multicolumn{1}{c}{--.3546} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.5431} & \multicolumn{1}{c}{--.4664} & \multicolumn{1}{c}{--.4583} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0018} & \multicolumn{1}{c}{+.0085} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0024} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--1.1521} & \multicolumn{1}{c}{--1.1228} & \multicolumn{1}{c}{--.9688} \\  
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean, indicated with a + or -- sign.}
\end{tablenotes}
\end{threeparttable}
\end{table}

`hd.ord` also performs worst for all data sets across both nominal variables. `amelia` and `mice` again perform best. `mice` does better for CCES, while `amelia` does better for Framing. Both perform equally well for ANES. As for the binary variables, the results for `hd.ord` consistently get slightly worse in the switch from one to two ordinal variables in `polr`-treatment: `r mult.mar.4.anes[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Inc"]`, `r mult.mar.4.cces[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Inc"]`, `r mult.mar.4.frame[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Inc"]` vs. `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Inc"]`, `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Inc"]`, `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Inc"]` for `Inc` and `r mult.mar.4.anes[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Age"]`, `r mult.mar.4.cces[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Age"]`, `r mult.mar.4.frame[mult.mar.4.meth == "hd.ord" & mult.mar.4.var == "Age"]` vs. `r mar.5.anes[mar.5.meth == "hd.ord" & mar.5.var == "Age"]`, `r mar.5.cces[mar.5.meth == "hd.ord" & mar.5.var == "Age"]`, `r mar.5.frame[mar.5.meth == "hd.ord" & mar.5.var == "Age"]` for `Age`.



```{r MULT MAR 11 Variables, include=FALSE}

mult.mar.11var.anes <- read.csv("data/anes/mar/results/anes.mar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.11var.cces <- read.csv("data/cces/mar/results/cces.mar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mar.11var.frame <- read.csv("data/framing/mar/results/framing.mar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mar.11var.anes$diff[mult.mar.11var.anes$method == "true"] <- mult.mar.11var.anes$value[mult.mar.11var.anes$method == "true"]
mult.mar.11var.cces$diff[mult.mar.11var.cces$method == "true"] <- mult.mar.11var.cces$value[mult.mar.11var.cces$method == "true"]
mult.mar.11var.frame$diff[mult.mar.11var.frame$method == "true"] <- mult.mar.11var.frame$value[mult.mar.11var.frame$method == "true"]

levels(mult.mar.11var.anes$method) <- levels(mult.mar.11var.cces$method) <- levels(mult.mar.11var.frame$method) <-
  levs


mult.un.meth <- mult.mar.11var.anes$method %>% unique
mult.un.meth.len <- mult.un.meth %>% length
mult.un.vars <- c(mult.mar.11var.anes$variable %>% as.character,
                  mult.mar.11var.cces$variable %>% as.character,
                  mult.mar.11var.frame$variable %>% as.character) %>%
  unique
mult.un.vars.len <- mult.un.vars %>% length
mult.un.anes.len <- mult.mar.11var.anes$variable %>% unique %>% length
mult.un.cces.var <- mult.mar.11var.cces$variable %>% unique %>% as.character
mult.un.cces.len <- mult.un.cces.var %>% length
mult.un.frame.var <- mult.mar.11var.frame$variable %>% unique %>% as.character
mult.un.frame.len <- mult.un.frame.var %>% length

mult.variable <- rep(mult.un.vars, each = mult.un.meth.len)
mult.method <- rep(mult.un.meth, mult.un.vars.len) %>% as.character
mult.meth.len <- mult.method %>% length

mult.mar.11var <- cbind(mult.method, mult.variable) %>% as.data.frame

mult.mar.11var$mult.anes.col <- c(mult.mar.11var.anes$diff,
                                  rep("---",
                                      mult.un.meth.len * (mult.un.vars.len - mult.un.anes.len)))
mult.mar.11var$mult.cces.col <- rep("---", mult.meth.len) %>% as.character
mult.mar.11var$mult.frame.col <- rep("---", mult.meth.len) %>% as.character

for(i in 1:(mult.un.cces.len)){
  mult.mar.11var$mult.cces.col[mult.mar.11var$mult.variable == mult.un.cces.var[i]] <- mult.mar.11var.cces$diff[mult.mar.11var.cces$variable == mult.un.cces.var[i]]
  mult.mar.11var$mult.frame.col[mult.mar.11var$mult.variable == mult.un.frame.var[i]] <- mult.mar.11var.frame$diff[mult.mar.11var.frame$variable == mult.un.frame.var[i]]
}

colnames(mult.mar.11var) <- col.names

# to make the in-text citations shorter
mult.mar.11.anes <- mult.mar.11var$ANES
mult.mar.11.cces <- mult.mar.11var$CCES
mult.mar.11.frame <- mult.mar.11var$Framing
mult.mar.11.meth <- mult.mar.11var$Method
mult.mar.11.var <- mult.mar.11var$Variable

stargazer(mult.mar.11var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 11 Variables with NA",
          label = "mult.mar.11var")


```

<!--
MAR 11 Var
Vars the same as for MAR and MNAR 12 Var, just without Interest (so no ordinal vars here)
	Binary
		Similar picture to MAR 4 Var, though overall hd.ord arguably closer now
		amelia and mice best again, often actually zero difference to true value
		Consistent with MAR 4 Var/5 Var development, hd.ord performs slightly worse with two ordinal variables when compared to MAR 12 Var:
		MAR 12 Var hd.ord: Dem .0005, .0004, .0004. Male .0001, .0003, .0000
		MAR 11 Var hd.ord: Dem .0005, .0005, .0005. Male .0001, .0004, .0002
	Ordinal framing
		hd.ord worst for Media and Participation, confirming previous results
		mice and amelia again by far best
		hd.ord gets slightly better when compared to MAR 12 Var:
		MAR 12 Var hd.ord: Media .0060. Participation .0027
		MAR 11 Var hd.ord: Media .0059, Participation .0026
	Nominal
		Same picture as before: hd.ord is worst across all ds
		Difference to hot.deck still there but less pronounced than for MAR 4 Var
		amelia is better for age, mice is better for Inc (except Inc ANES, .0027 vs. .0018)
		hd.ord consistently gets slightly worse when compared to MAR 12 Var:		
		MAR 12 Var hd.ord: Inc .0591, .0212, .0089. Age .1835, .1435, .1592 
		MAR 11 Var hd.ord: Inc .0657, .0241, .0095. Age .1951, .1532, .1640
-->

Table \ref{mult.mar.11var} shows the results of imputing all data sets with two `polr`-treated variables MAR for 11 amputed variables. A similar picture fo Table \ref{mult.mar.4var} emerges for the binary variables, with `amelia` and `mice` once more displaying the best results, though `hd.ord` appears to perform somewhat closer here. Consistent with the deterioriation of `hd.ord` results from Table \ref{mar.5var} to Table \ref{mult.mar.4var}, `hd.ord` again consistently performs slightly worse when compared to the MAR analysis with 12 amputed variables and only `Education` treated by `polr`: `r mult.mar.11.anes[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Dem"]`, `r mult.mar.11.cces[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Dem"]`, `r mult.mar.11.frame[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Dem"]` vs. `r mar.12.anes[mar.12.meth == "hd.ord" & mar.12.var == "Dem"]`, `r mar.12.cces[mar.12.meth == "hd.ord" & mar.12.var == "Dem"]`, `r mar.12.frame[mar.12.meth == "hd.ord" & mar.12.var == "Dem"]` for `Dem` and `r mult.mar.11.anes[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Male"]`, `r mult.mar.11.cces[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Male"]`, `r mult.mar.11.frame[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Male"]` vs. `r mar.12.anes[mar.12.meth == "hd.ord" & mar.12.var == "Male"]`, `r mar.12.cces[mar.12.meth == "hd.ord" & mar.12.var == "Male"]`, `r mar.12.frame[mar.12.meth == "hd.ord" & mar.12.var == "Male"]` for `Male`.

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MAR, 11 Variables with NA} 
  \label{mult.mar.11var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{+.0005} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0200} & \multicolumn{1}{c}{--.0213} & \multicolumn{1}{c}{--.0294} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0254} & \multicolumn{1}{c}{--.0350} & \multicolumn{1}{c}{--.0174} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0346} & \multicolumn{1}{c}{--.0114} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0657} & \multicolumn{1}{c}{--.0241} & \multicolumn{1}{c}{--.0095} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0018} & \multicolumn{1}{c}{--.0007} & \multicolumn{1}{c}{--.0004} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.6432} & \multicolumn{1}{c}{--.2888} & \multicolumn{1}{c}{--.0983} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0887} & \multicolumn{1}{c}{--.0704} & \multicolumn{1}{c}{--.1379} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1951} & \multicolumn{1}{c}{--.1532} & \multicolumn{1}{c}{--.1640} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{+.0010} & \multicolumn{1}{c}{--.0021} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0016} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{+.0022} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.8025} & \multicolumn{1}{c}{--.4330} & \multicolumn{1}{c}{--.5290} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0103} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{--.0134} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0007} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0008} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0008} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0007} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0109} & \multicolumn{1}{c}{--.0328} & \multicolumn{1}{c}{--.0159} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0174} & \multicolumn{1}{c}{--.0241} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0390} & \multicolumn{1}{c}{--.0324} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0005} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0341} & \multicolumn{1}{c}{--.0295} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{+.0002} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0186} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0007} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0310} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0113} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0146} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0091} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0006} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0004} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0373} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0001} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0047} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0059} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0002} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0921} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0019} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0002} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{+.0000} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0963} \\
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize

The same can be observed for the nominal variables, with `hd.ord` again claiming last place across all data sets. The difference to `hot.deck` is still there but less pronounced than in Table \ref{mult.mar.4var}. `amelia` does best for `Age` while `mice` performs better for `Inc`, with the exception of the ANES (`r mult.mar.11.anes[mult.mar.11.meth == "mice" & mult.mar.11.var == "Inc"]` `mice` vs. `r mult.mar.11.anes[mult.mar.11.meth == "amelia" & mult.mar.11.var == "Inc"]` `amelia`). As for the binary variables, `hd.ord` also consistently performs slightly worse when compared to the MAR analysis with 12 amputed variables and only `Education` treated by `polr`: `r mult.mar.11.anes[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Inc"]`, `r mult.mar.11.cces[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Inc"]`, `r mult.mar.11.frame[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Inc"]` vs. `r mar.12.anes[mar.12.meth == "hd.ord" & mar.12.var == "Inc"]`, `r mar.12.cces[mar.12.meth == "hd.ord" & mar.12.var == "Inc"]`, `r mar.12.frame[mar.12.meth == "hd.ord" & mar.12.var == "Inc"]` for `Inc` and `r mult.mar.11.anes[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Age"]`, `r mult.mar.11.cces[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Age"]`, `r mult.mar.11.frame[mult.mar.11.meth == "hd.ord" & mult.mar.11.var == "Age"]` vs. `r mar.12.anes[mar.12.meth == "hd.ord" & mar.12.var == "Age"]`, `r mar.12.cces[mar.12.meth == "hd.ord" & mar.12.var == "Age"]`, `r mar.12.frame[mar.12.meth == "hd.ord" & mar.12.var == "Age"]` for `Age`.



```{r MULT MNAR 4 Variables, include=FALSE}

mult.mnar.4var.anes <- read.csv("data/anes/mnar/results/anes.mnar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.4var.cces <- read.csv("data/cces/mnar/results/cces.mnar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.4var.frame <- read.csv("data/framing/mnar/results/framing.mnar.mult.results.4var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mnar.4var.anes$diff[mult.mnar.4var.anes$method == "true"] <- mult.mnar.4var.anes$value[mult.mnar.4var.anes$method == "true"]
mult.mnar.4var.cces$diff[mult.mnar.4var.cces$method == "true"] <- mult.mnar.4var.cces$value[mult.mnar.4var.cces$method == "true"]
mult.mnar.4var.frame$diff[mult.mnar.4var.frame$method == "true"] <- mult.mnar.4var.frame$value[mult.mnar.4var.frame$method == "true"]

levels(mult.mnar.4var.anes$method) <- levels(mult.mnar.4var.cces$method) <- levels(mult.mnar.4var.frame$method) <-
  levs

mult.mnar.4var <- cbind(mult.mnar.4var.anes[, c(1,2,4)], mult.mnar.4var.cces[,4], mult.mnar.4var.frame[,4])
colnames(mult.mnar.4var) <- col.names

# to make the in-text citations shorter
mult.mnar.4.anes <- mult.mnar.4var$ANES
mult.mnar.4.cces <- mult.mnar.4var$CCES
mult.mnar.4.frame <- mult.mnar.4var$Framing
mult.mnar.4.meth <- mult.mnar.4var$Method
mult.mnar.4.var <- mult.mnar.4var$Variable

stargazer(mult.mnar.4var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 4 Variables with NA",
          label = "mult.mnar.4var")


```

<!--
MNAR 4 Var
Vars the same as for MAR 4 Var
	Binary
		hd.ord equally close to amelia and mice as for MNAR 5 Var, sometimes more (.0131 hd.ord vs. .0130 mice Dem CCES), sometimes less (.0155 hd.ord vs. .0127 mice Dem ANES). hd.ord actually best of all methods for framing for both vars, but overall amelia and mice perform better
		na.omit not as close as for MNAR 5 Var
		hd.ord consistently gets slightly worse when compared to MNAR 5 Var:		
		MNAR 5 Var hd.ord: Dem .0120, .0105, .0033. Male .0133, .0124, .0125
		MNAR 4 Var hd.ord: Dem .0155, .0131, .0042. Male .0172, .0160, .0157
	Nominal
		Consistent with previous analyses. 
		na.omit better than hd.ord for Age for all three ds and for Inc ANES
		hd.ord consistently gets slightly worse when compared to MNAR 5 Var:		
		MNAR 5 Var hd.ord: Inc .2554, .1038, .0648. Age .7415, .5929, .7477
		MNAR 4 Var hd.ord: Inc .3174, .1303, .0812. Age .8997, .7259, .9349
-->

Table \ref{mult.mnar.4var} shows the results of imputing all data sets with two `polr`-treated variables MNAR for four amputed variables. For the binary variables, `hd.ord` performs on the same level as `amelia` and `mice` when compared to the MNAR analysis of five imputed variables with only `Education` treated by `polr`; sometimes more (`r mult.mnar.4.cces[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Dem"]` `hd.ord` vs. `r mult.mnar.4.cces[mult.mnar.4.meth == "mice" & mult.mnar.4.var == "Dem"]` `mice` CCES `Dem`), sometimes less so (`r mult.mnar.4.anes[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Dem"]` `hd.ord` vs. `r mult.mnar.4.anes[mult.mnar.4.meth == "mice" & mult.mnar.4.var == "Dem"]` `mice` ANES `Dem`). `hd.ord` actually shows the best results of all methods for Framing for both variables. `na.omit` does not perform as well as it does in Table \ref{mnar.5var}. `hd.ord` again consistently performs slightly worse with the two-ordinal-variable-`polr`-treatment: `r mult.mnar.4.anes[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Dem"]`,`r mult.mnar.4.cces[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Dem"]`, `r mult.mnar.4.frame[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Dem"]` vs. `r mnar.5.anes[mnar.5.meth == "hd.ord" & mnar.5.var == "Dem"]`, `r mnar.5.cces[mnar.5.meth == "hd.ord" & mnar.5.var == "Dem"]`, `r mnar.5.frame[mnar.5.meth == "hd.ord" & mnar.5.var == "Dem"]` for `Dem` and `r mult.mnar.4.anes[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Male"]`, `r mult.mnar.4.cces[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Male"]`, `r mult.mnar.4.frame[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Male"]` vs. `r mnar.5.anes[mnar.5.meth == "hd.ord" & mnar.5.var == "Male"]`, `r mnar.5.cces[mnar.5.meth == "hd.ord" & mnar.5.var == "Male"]`, `r mnar.5.frame[mnar.5.meth == "hd.ord" & mnar.5.var == "Male"]` for `Male`.

\begin{table}[!htbp] \centering 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 4 Variables with NA} 
  \label{mult.mnar.4var} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0142} & \multicolumn{1}{c}{--.0133} & \multicolumn{1}{c}{--.0043} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0155} & \multicolumn{1}{c}{--.0131} & \multicolumn{1}{c}{--.0042} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0136} & \multicolumn{1}{c}{--.0131} & \multicolumn{1}{c}{--.0059} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0127} & \multicolumn{1}{c}{--.0130} & \multicolumn{1}{c}{--.0046} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0211} & \multicolumn{1}{c}{--.0185} & \multicolumn{1}{c}{--.0207} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0180} & \multicolumn{1}{c}{--.0162} & \multicolumn{1}{c}{--.0167} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0172} & \multicolumn{1}{c}{--.0160} & \multicolumn{1}{c}{--.0157} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0170} & \multicolumn{1}{c}{--.0154} & \multicolumn{1}{c}{--.0170} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0170} & \multicolumn{1}{c}{--.0153} & \multicolumn{1}{c}{--.0172} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0233} & \multicolumn{1}{c}{--.0241} & \multicolumn{1}{c}{--.0169} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2481} & \multicolumn{1}{c}{--.1034} & \multicolumn{1}{c}{--.0728} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.3174} & \multicolumn{1}{c}{--.1303} & \multicolumn{1}{c}{--.0812} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1555} & \multicolumn{1}{c}{--.0741} & \multicolumn{1}{c}{--.0589} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1568} & \multicolumn{1}{c}{--.0730} & \multicolumn{1}{c}{--.0565} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.3114} & \multicolumn{1}{c}{--.1513} & \multicolumn{1}{c}{--.0852} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6020} & \multicolumn{1}{c}{--.4844} & \multicolumn{1}{c}{--.8613} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.8997} & \multicolumn{1}{c}{--.7259} & \multicolumn{1}{c}{--.9349} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3103} & \multicolumn{1}{c}{--.2831} & \multicolumn{1}{c}{--.3702} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2994} & \multicolumn{1}{c}{--.2702} & \multicolumn{1}{c}{--.3705} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.6726} & \multicolumn{1}{c}{--.6482} & \multicolumn{1}{c}{--.6213} \\
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean, indicated with a + or -- sign.}
\end{tablenotes}
\end{threeparttable}
\end{table}

The results for the nominal variables are consistent with the previous analyses. In addition, note that `na.omit` performs better than `hd.ord` for `Age` across all three data sets and for ANES `Inc`. Once more, `hd.ord` consistently performs slightly worse with more than two ordinal variables: `r mult.mnar.4.anes[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Inc"]`, `r mult.mnar.4.cces[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Inc"]`, `r mult.mnar.4.frame[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Inc"]` vs. `r mnar.5.anes[mnar.5.meth == "hd.ord" & mnar.5.var == "Inc"]`, `r mnar.5.cces[mnar.5.meth == "hd.ord" & mnar.5.var == "Inc"]`, `r mnar.5.frame[mnar.5.meth == "hd.ord" & mnar.5.var == "Inc"]` for `Inc` and `r mult.mnar.4.anes[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Age"]`, `r mult.mnar.4.cces[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Age"]`, `r mult.mnar.4.frame[mult.mnar.4.meth == "hd.ord" & mult.mnar.4.var == "Age"]` vs. `r mnar.5.anes[mnar.5.meth == "hd.ord" & mnar.5.var == "Age"]`, `r mnar.5.cces[mnar.5.meth == "hd.ord" & mnar.5.var == "Age"]`, `r mnar.5.frame[mnar.5.meth == "hd.ord" & mnar.5.var == "Age"]` for `Age`.


```{r MULT MNAR 11 Variables, include=FALSE}

mult.mnar.11var.anes <- read.csv("data/anes/mnar/results/anes.mnar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.11var.cces <- read.csv("data/cces/mnar/results/cces.mnar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus
mult.mnar.11var.frame <- read.csv("data/framing/mnar/results/framing.mnar.mult.results.11var.1000n.1000it.20perc.csv") %>% .[,-1] %>% dropZero.addPlus

mult.mnar.11var.anes$diff[mult.mnar.11var.anes$method == "true"] <- mult.mnar.11var.anes$value[mult.mnar.11var.anes$method == "true"]
mult.mnar.11var.cces$diff[mult.mnar.11var.cces$method == "true"] <- mult.mnar.11var.cces$value[mult.mnar.11var.cces$method == "true"]
mult.mnar.11var.frame$diff[mult.mnar.11var.frame$method == "true"] <- mult.mnar.11var.frame$value[mult.mnar.11var.frame$method == "true"]

levels(mult.mnar.11var.anes$method) <- levels(mult.mnar.11var.cces$method) <- levels(mult.mnar.11var.frame$method) <-
  levs


mult.un.meth <- mult.mnar.11var.anes$method %>% unique
mult.un.meth.len <- mult.un.meth %>% length
mult.un.vars <- c(mult.mnar.11var.anes$variable %>% as.character,
                  mult.mnar.11var.cces$variable %>% as.character,
                  mult.mnar.11var.frame$variable %>% as.character) %>%
  unique
mult.un.vars.len <- mult.un.vars %>% length
mult.un.anes.len <- mult.mnar.11var.anes$variable %>% unique %>% length
mult.un.cces.var <- mult.mnar.11var.cces$variable %>% unique %>% as.character
mult.un.cces.len <- mult.un.cces.var %>% length
mult.un.frame.var <- mult.mnar.11var.frame$variable %>% unique %>% as.character
mult.un.frame.len <- mult.un.frame.var %>% length

mult.variable <- rep(mult.un.vars, each = mult.un.meth.len)
mult.method <- rep(mult.un.meth, mult.un.vars.len) %>% as.character
mult.meth.len <- mult.method %>% length

mult.mnar.11var <- cbind(mult.method, mult.variable) %>% as.data.frame

mult.mnar.11var$mult.anes.col <- c(mult.mnar.11var.anes$diff,
                                  rep("---",
                                      mult.un.meth.len * (mult.un.vars.len - mult.un.anes.len)))
mult.mnar.11var$mult.cces.col <- rep("---", mult.meth.len) %>% as.character
mult.mnar.11var$mult.frame.col <- rep("---", mult.meth.len) %>% as.character

for(i in 1:(mult.un.cces.len)){
  mult.mnar.11var$mult.cces.col[mult.mnar.11var$mult.variable == mult.un.cces.var[i]] <- mult.mnar.11var.cces$diff[mult.mnar.11var.cces$variable == mult.un.cces.var[i]]
  mult.mnar.11var$mult.frame.col[mult.mnar.11var$mult.variable == mult.un.frame.var[i]] <- mult.mnar.11var.frame$diff[mult.mnar.11var.frame$variable == mult.un.frame.var[i]]
}

colnames(mult.mnar.11var) <- col.names

# to make the in-text citations shorter
mult.mnar.11.anes <- mult.mnar.11var$ANES
mult.mnar.11.cces <- mult.mnar.11var$CCES
mult.mnar.11.frame <- mult.mnar.11var$Framing
mult.mnar.11.meth <- mult.mnar.11var$Method
mult.mnar.11.var <- mult.mnar.11var$Variable

stargazer(mult.mnar.11var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 11 Variables with NA",
          label = "mult.mnar.11var")

```

<!--
MNAR 11 Var
Vars the same as for MAR 11 Var
	Binary
		amelia and mice perform better, but often not by much. Occasionally, hd.ord eclipses them (.0057 hd.ord vs. .0060 mice Male ANES; .0057 hd.ord vs. .0059 amelia Male framing)
		hd.ord consistently gets slightly worse when compared to MNAR 12 Var:		
		MNAR 12 Var hd.ord: Dem .0049, .0049, .0013. Male .0053, .0051,. 0051
		MNAR 11 Var hd.ord: Dem .0053, .0053, .0024. Male .0057, .0056, .0057
	Ordinal framing
		hd.ord worst for Media but better than hot.deck for Participation
		mice and amelia performs best by a significant margin
		na.omit as far off as for MNAR 12 Var
		hd.ord consistently gets slightly worse when compared to MNAR 12 Var:		
		MNAR 12 Var hd.ord: Media .0152, Participation .0115
		MNAR 11 Var hd.ord: Media .0164. Participation .0130
	Nominal
		Consistent with previous analyses
		na.omit better than hd.ord for Age for all ds. na.omit also best overall across all methods for Age CCES
		hd.ord consistently gets slightly worse when compared to MNAR 12 Var:		
		MNAR 12 Var hd.ord: Inc .1046, .0421, .0262. Age .3081, .2251, .2989
		MNAR 11 Var hd.ord: Inc .1142, .0473, .0291. Age .3329, .2424, .3271
-->

Table \ref{mult.mnar.11var} shows the results of imputing all data sets with two `polr`-treated variables MNAR for 11 amputed variables. For the binary variables, `amelia` and `mice` perform better, but often not by much. Occasionally, `hd.ord` eclipses them (`r mult.mnar.11.anes[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Male"]` `hd.ord` vs. `r mult.mnar.11.anes[mult.mnar.11.meth == "mice" & mult.mnar.11.var == "Male"]` `mice` ANES `Male`; `r mult.mnar.11.frame[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Male"]` `hd.ord` vs. `r mult.mnar.11.frame[mult.mnar.11.meth == "amelia" & mult.mnar.11.var == "Male"]` `amelia` Framing `Male`). As was the case in the comparison between the MNAR analysis with four amputed variables and the MNAR analyis with five amputed variables, `hd.ord` consistently demonstrates slightly worse results in the switch from 12 (Table \ref{mnar.12var}) to 11 and one to two `polr`-treated variables: `r mult.mnar.11.anes[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Dem"]`, `r mult.mnar.11.cces[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Dem"]`, `r mult.mnar.11.frame[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Dem"]` vs. `r mnar.12.anes[mnar.12.meth == "hd.ord" & mnar.12.var == "Dem"]`, `r mnar.12.cces[mnar.12.meth == "hd.ord" & mnar.12.var == "Dem"]`, `r mnar.12.frame[mnar.12.meth == "hd.ord" & mnar.12.var == "Dem"]` for `Dem` and `r mult.mnar.11.anes[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Male"]`, `r mult.mnar.11.cces[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Male"]`, `r mult.mnar.11.frame[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Male"]` vs. `r mnar.12.anes[mnar.12.meth == "hd.ord" & mnar.12.var == "Male"]`, `r mnar.12.cces[mnar.12.meth == "hd.ord" & mnar.12.var == "Male"]`, `r mnar.12.frame[mnar.12.meth == "hd.ord" & mnar.12.var == "Male"]` for `Male`.

\ssp

\footnotesize

\begin{longtable}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
  \caption{Accuracy of Multiple Imputation Methods. Two Ordinal Variables (Education, Interest), MNAR, 11 Variables with NA} 
  \label{mult.mnar.11var} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.3420} & \multicolumn{1}{c}{.3770} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0022} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0048} & \multicolumn{1}{c}{--.0019} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0097} & \multicolumn{1}{c}{--.0097} & \multicolumn{1}{c}{--.0109} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.4890} & \multicolumn{1}{c}{.4830} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0061} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{--.0061} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{--.0056} & \multicolumn{1}{c}{--.0057} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0060} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{--.0059} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0060} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{--.0060} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0088} & \multicolumn{1}{c}{--.0116} & \multicolumn{1}{c}{--.0068} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{16.6140} & \multicolumn{1}{c}{6.4810} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0841} & \multicolumn{1}{c}{--.0349} & \multicolumn{1}{c}{--.0258} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1142} & \multicolumn{1}{c}{--.0473} & \multicolumn{1}{c}{--.0291} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0540} & \multicolumn{1}{c}{--.0250} & \multicolumn{1}{c}{--.0206} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0549} & \multicolumn{1}{c}{--.0249} & \multicolumn{1}{c}{--.0199} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.2112} & \multicolumn{1}{c}{--.0982} & \multicolumn{1}{c}{--.0342} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{50.0410} & \multicolumn{1}{c}{52.8230} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2124} & \multicolumn{1}{c}{--.1607} & \multicolumn{1}{c}{--.2819} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3329} & \multicolumn{1}{c}{--.2424} & \multicolumn{1}{c}{--.3271} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1194} & \multicolumn{1}{c}{--.1135} & \multicolumn{1}{c}{--.1257} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.1141} & \multicolumn{1}{c}{--.1102} & \multicolumn{1}{c}{--.1244} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.2978} & \multicolumn{1}{c}{--.0974} & \multicolumn{1}{c}{--.2074} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{.0790} & \multicolumn{1}{c}{.0950} & \multicolumn{1}{c}{.0690} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0036} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0031} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0041} & \multicolumn{1}{c}{--.0011} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Black} & \multicolumn{1}{c}{--.0050} & \multicolumn{1}{c}{--.0066} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{.6610} & \multicolumn{1}{c}{.4370} & \multicolumn{1}{c}{.7430} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0036} & \multicolumn{1}{c}{--.0058} & \multicolumn{1}{c}{--.0024} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0034} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Empl} & \multicolumn{1}{c}{--.0022} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{--.0033} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{.6460} & \multicolumn{1}{c}{.6420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Religious} & \multicolumn{1}{c}{--.0055} & \multicolumn{1}{c}{--.0077} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{.5290} & \multicolumn{1}{c}{.6310} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{--.0043} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0042} & \multicolumn{1}{c}{--.0040} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0046} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Married} & \multicolumn{1}{c}{--.0120} & \multicolumn{1}{c}{--.0095} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{.6820} & \multicolumn{1}{c}{.7010} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{--.0035} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0031} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0030} & \multicolumn{1}{c}{--.0033} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{OwnHome} & \multicolumn{1}{c}{--.0112} & \multicolumn{1}{c}{--.0088} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{.0830} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0047} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0045} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0044} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Rally} & \multicolumn{1}{c}{--.0080} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{.1390} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0060} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0054} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0053} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Donate} & \multicolumn{1}{c}{--.0122} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0420} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0028} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Gay} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0037} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.1910} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0067} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0064} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0057} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0056} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{StudLoans} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0082} & \multicolumn{1}{c}{---} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0550} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0027} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0028} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0012} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Hisp} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0037} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.3560} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0067} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0061} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0055} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0054} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Official} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0139} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.0440} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0026} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0025} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0021} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Stud} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0021} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{1.7240} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0156} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0164} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0110} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0110} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Media} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0345} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{.9540} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0138} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0130} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0111} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0105} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Participation} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{--.0348} \\ 
\hline \\[-1.8ex] 
\end{longtable} 

\dsp

\normalsize

Finally, the results for the nominal variables confirm previous results, with `amelia` and `mice` demonstrating the best performance. In addition, note that `na.omit` delivers better results than `hd.ord` for `Age` for all data sets and represents the best method for CCES `Age`. Similar to the MNAR results for four variables, the performance of `hd.ord` in the MNAR analysis of 11 variables deteriorates in the switch from one to two ordinal variables: `r mult.mnar.11.anes[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Inc"]`, `r mult.mnar.11.cces[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Inc"]`, `r mult.mnar.11.frame[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Inc"]` vs. `r mnar.12.anes[mnar.12.meth == "hd.ord" & mnar.12.var == "Inc"]`, `r mnar.12.cces[mnar.12.meth == "hd.ord" & mnar.12.var == "Inc"]`, `r mnar.12.frame[mnar.12.meth == "hd.ord" & mnar.12.var == "Inc"]` for `Inc` and `r mult.mnar.11.anes[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Age"]`, `r mult.mnar.11.cces[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Age"]`, `r mult.mnar.11.frame[mult.mnar.11.meth == "hd.ord" & mult.mnar.11.var == "Age"]` vs. `r mnar.12.anes[mnar.12.meth == "hd.ord" & mnar.12.var == "Age"]`, `r mnar.12.cces[mnar.12.meth == "hd.ord" & mnar.12.var == "Age"]`, `r mnar.12.frame[mnar.12.meth == "hd.ord" & mnar.12.var == "Age"]` for `Age`.




### Increased Percentage of Missingness {#ordmiss-results-increaseNA}

```{r Increasing Missingness Percentage, include=FALSE}

mar.5var.frame.20 <- mar.5var.frame
mar.5var.frame.50 <- read.csv("data/framing/mar/results/framing.mar.results.5var.1000n.1000it.50perc.csv") %>% .[,-1] %>% dropZero.addPlus
mar.5var.frame.80 <- read.csv("data/framing/mar/results/framing.mar.results.5var.1000n.1000it.80perc.csv") %>% .[,-1] %>% dropZero.addPlus

mar.5var.frame.20$diff[mar.5var.frame.20$method == "true"] <- 
  mar.5var.frame.50$diff[mar.5var.frame.50$method == "true"] <- 
  mar.5var.frame.80$diff[mar.5var.frame.80$method == "true"] <- 
  mar.5var.frame.20$value[mar.5var.frame.20$method == "true"]

levels(mar.5var.frame.20$method) <- 
  levels(mar.5var.frame.50$method) <- 
  levels(mar.5var.frame.80$method) <- 
  levs

mar.5var.old.frame <- cbind(mar.5var.frame.20[,c(1,2,4)], mar.5var.frame.50[,4], mar.5var.frame.80[,4])
colnames(mar.5var.old.frame) <- c("Method", "Variable", "20% NA", "50% NA", "80% NA")

# to make the in-text citations shorter
frame.NA20 <- mar.5var.old.frame$`20% NA`
frame.NA50 <- mar.5var.old.frame$`50% NA`
frame.NA80 <- mar.5var.old.frame$`80% NA`
frame.80.meth <- mar.5var.old.frame$Method
frame.80.var <- mar.5var.old.frame$Variable

stargazer(mar.5var.old.frame, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          digits = 4,
          title = "Accuracy of Multiple Imputation Methods for Increasing Percentages of Missing Data (Framing Experiment Data)",
          label = "mar.5var.old.frame")

```

<!--
Increased Missingness
Framing MAR 5 Var
	Binary
		hd.ord worst for all percentages for all vars
		hot.deck outperforms amelia and mice for Dem and Male CCES
		amelia and mice virtually identical
	Ordinal
		hd.ord worst for all percentages for all vars
		amelia and mice far best and virtually identical
	Nominal
		hd.ord worst for all percentages for all vars
		amelia and mice far best
		amelia outperforms mice for all percentages for all vars	
-->

This brief section shows the imputation results when the percentage of missingness is increased. I conduct this here MAR for five variables in the Framing data. The results are shown in Table \ref{mar.5var.old.frame}. As was to be expected at this point, `hd.ord` displays the worst performance for all percentages for all binary variables. 

\begin{table}[!ht] \centering 
  \caption{Accuracy of Multiple Imputation Methods for Increasing Percentages of Missing Data (Framing Experiment Data)} 
  \label{mar.5var.old.frame} 
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{20\% NA} & \multicolumn{1}{c}{50\% NA} & \multicolumn{1}{c}{80\% NA} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{.4660} & \multicolumn{1}{c}{.4660} & \multicolumn{1}{c}{.4660} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0016} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0008} & \multicolumn{1}{c}{+.0018} & \multicolumn{1}{c}{+.0037} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0004} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{+.0004} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Dem} & \multicolumn{1}{c}{--.0340} & \multicolumn{1}{c}{--.0841} & \multicolumn{1}{c}{--.1393} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{.5260} & \multicolumn{1}{c}{.5260} & \multicolumn{1}{c}{.5260} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0004} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0005} & \multicolumn{1}{c}{+.0009} & \multicolumn{1}{c}{+.0014} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{+.0000} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0001} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{--.0006} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{--.0256} & \multicolumn{1}{c}{--.0632} & \multicolumn{1}{c}{--.1051} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{3.2170} & \multicolumn{1}{c}{3.2170} & \multicolumn{1}{c}{3.2170} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0213} & \multicolumn{1}{c}{--.0604} & \multicolumn{1}{c}{--.0908} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0248} & \multicolumn{1}{c}{--.0679} & \multicolumn{1}{c}{--.1007} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0002} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{+.0003} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0003} & \multicolumn{1}{c}{--.0004} & \multicolumn{1}{c}{+.0001} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Interest} & \multicolumn{1}{c}{--.0714} & \multicolumn{1}{c}{--.1833} & \multicolumn{1}{c}{--.3219} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{3.0890} & \multicolumn{1}{c}{3.0890} & \multicolumn{1}{c}{3.0890} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0119} & \multicolumn{1}{c}{--.0371} & \multicolumn{1}{c}{--.0594} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.0192} & \multicolumn{1}{c}{--.0550} & \multicolumn{1}{c}{--.0805} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0003} & \multicolumn{1}{c}{+.0001} & \multicolumn{1}{c}{+.0009} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{+.0014} & \multicolumn{1}{c}{+.0028} & \multicolumn{1}{c}{+.0039} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Inc} & \multicolumn{1}{c}{--.1367} & \multicolumn{1}{c}{--.3076} & \multicolumn{1}{c}{--.4850} \\ 
\multicolumn{1}{c}{true} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{37.9120} & \multicolumn{1}{c}{37.9120} & \multicolumn{1}{c}{37.9120} \\ 
\multicolumn{1}{c}{hot.deck} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3650} & \multicolumn{1}{c}{--1.0406} & \multicolumn{1}{c}{--1.5789} \\ 
\multicolumn{1}{c}{hd.ord} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.3923} & \multicolumn{1}{c}{--1.1319} & \multicolumn{1}{c}{--1.6962} \\ 
\multicolumn{1}{c}{amelia} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0039} & \multicolumn{1}{c}{+.0043} & \multicolumn{1}{c}{--.0005} \\ 
\multicolumn{1}{c}{mice} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--.0049} & \multicolumn{1}{c}{+.0047} & \multicolumn{1}{c}{+.0034} \\ 
\multicolumn{1}{c}{na.omit} & \multicolumn{1}{c}{Age} & \multicolumn{1}{c}{--1.0641} & \multicolumn{1}{c}{--2.3051} & \multicolumn{1}{c}{--3.4885} \\  
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\footnotesize{\textit{Note:} Each \texttt{true} value shows the true variable mean. All other values show the differences between the imputation means and the true mean, indicated with a + or -- sign.}
\end{tablenotes}
\end{threeparttable}
\end{table}

`amelia` and `mice` show virtually identical results. Note that `hot.deck` appears to outperform `amelia` and `mice` for CCES `Dem` and `Male`. `hd.ord` also represents the worst method for all percentages for all ordinal and nominal variables. `amelia` and `mice` show virtually identical results and far outperform the other methods for the ordinal variables. Note that `amelia` also consistently outperforms `mice` for all percentages for all nominal variables.




### Speed {#ordmiss-results-speed}

```{r Runtimes 5/12 Variables MAR, include=FALSE}

run.5var.anes <- read.csv("data/anes/mar/runtimes/anes.mar.runtime.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.5var.cces <- read.csv("data/cces/mar/runtimes/cces.mar.runtime.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.5var.frame <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.5var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]

run.12var.anes <- read.csv("data/anes/mar/runtimes/anes.mar.runtime.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.12var.cces <- read.csv("data/cces/mar/runtimes/cces.mar.runtime.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.12var.frame <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.12var.1000n.1000it.20perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]

run.5var.12var <- data.frame(matrix(NA, 4, 7))
colnames(run.5var.12var) <- c("Method", "ANES5", "CCES5", "Framing5", "ANES12", "CCES12", "Framing12")
run.5var.12var$Method <- run.5var.anes$V2

runs <- list(run.5var.anes, run.5var.cces, run.5var.frame,
             run.12var.anes, run.12var.cces, run.12var.frame)

for(x in 1:length(runs)){
  run.5var.12var[1:4, x+1] <- runs[[x]][,2]
}

run.meth <- run.5var.12var$Method

# so I can use how much slower amelia is than hd.ord
var.hd.am.div <- sapply(2:7, 
                    function(x)
                      run.5var.12var[run.meth == "amelia", x] / 
                      run.5var.12var[run.meth == "hd.ord", x]) 

# so I can use how much slower mice is than hd.ord
var.hd.mi.div <- sapply(2:7, 
                    function(x)
                      run.5var.12var[run.meth == "mice", x] / 
                      run.5var.12var[run.meth == "hd.ord", x]) 

stargazer(run.5var.12var, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          title = "Runtimes of Multiple Imputation Methods (in Minutes) by Number of Imputed Variables",
          label = "runtimes5var12var")

```

<!--
Speed
Analyzed by number of imputed variables for all ds (MAR)
	hd.ord and hot.deck much faster and virtually identical
	amelia consistently several times slower for all ds for both numbers of imputed vars
	mice much, much worse than all other methods across the board
Analyzed by percentage of missingness for framing data (MAR 5 Var)
	amelia and mice get closer as the percentage of missingess increases
-->

This section shows the running times for all methods. Specifically, I outline the speed differences by the number of imputed variables for all data sets (Table \ref{runtimes5var12var}) and by the percentage of missingness for the Framing data (Table \ref{run.all.perc}). Both analyses are conducted MAR, with the latter only for five imputed variables. All running times are given in minutes and apply to all 1,000 amputation/imputation iterations combined.

We can see in Table \ref{runtimes5var12var} that `hd.ord` and `hot.deck` show virtually identical running times for all data sets for both numbers of imputed variables. This is to be expected as both methods are very similar in terms of their code build-up. More importantly, however, we observe that both methods are much faster than `amelia` and `mice`: `amelia` is at least `r var.hd.am.div %>% min %>% round(., digits = 1)` times slower than `hd.ord` (for the Framing data for both numbers of imputed variables). The highest difference amounts to `r var.hd.am.div %>% max %>% round(., digits = 1)` (for the CCES data with 12 imputed variables). `mice`, however, shows by far the highest running times. At its worst, `mice` is `r var.hd.mi.div %>% max %>% round(., digits = 1)` times slower than `hd.ord` (for the CCES data with 12 imputed variables). At its best, this deficit still amounts `r var.hd.mi.div %>% min %>% round(., digits = 1)` times slower (for the Framing data with five imputed variables). 

\begin{table}[!htbp] \centering 
  \caption{Runtimes of Multiple Imputation Methods (in Minutes) by Number of Imputed Variables} 
  \label{runtimes5var12var} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{5 Variables with NA} & \multicolumn{3}{c}{12 Variables with NA}\\ 
\cline{2-7}  \\[-1.8ex]
 & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} & \multicolumn{1}{c}{ANES} & \multicolumn{1}{c}{CCES} & \multicolumn{1}{c}{Framing} \\ 
\cline{2-4} 
\cline{5-7}  \\[-1.8ex]
\multicolumn{1}{c}{hd.ord} & 2.632 & 2.778 & 2.559 & 2.614 & 2.679 & 2.555 \\ 
\multicolumn{1}{c}{hot.deck} & 2.628 & 2.786 & 2.567 & 2.640 & 2.690 & 2.582 \\ 
\multicolumn{1}{c}{amelia} & 9.052 & 10.611 & 8.079 & 9.038 & 10.345 & 8.109 \\ 
\multicolumn{1}{c}{mice} & 50.445 & 57.205 & 48.436 & 104.143 & 113.390 & 103.953 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}


```{r Runtimes Increased Missingness MAR Code, include=FALSE}

run.20 <- run.5var.frame
run.50 <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.5var.1000n.1000it.50perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]
run.80 <- read.csv("data/framing/mar/runtimes/framing.mar.runtime.5var.1000n.1000it.80perc.csv") %>% .[,-1] %>% .[, order(ncol(.):1)]

run.all.perc <- cbind(run.20$V1, run.50$V1, run.80$V1) %>% as.data.frame %>% round(., digits = 2)
run.all.perc$V4 <- run.20$V2 %>% as.character
run.all.perc <- run.all.perc[,c(4, 1:3)]
colnames(run.all.perc) <- c("Method", "20% NA", "50% NA", "80% NA")

perc.hd.am.div <- run.all.perc[3,2:4] %>% as.numeric / run.all.perc[1,2:4] %>% as.numeric
perc.hd.mi.div <- run.all.perc[4,2:4] %>% as.numeric / run.all.perc[1,2:4] %>% as.numeric

```


Table \ref{run.all.perc} shows that `hd.ord` and `hot.deck` remain the fastest methods across all percentages of missingness, but the gap to `amelia` and `mice` narrows as the missingness increases. `amelia` improves from `r perc.hd.am.div %>% max %>% round(., digits = 1)` times slower than `hd.ord` for 20 percent NA to `r perc.hd.am.div %>% min %>% round(., digits = 1)` times slower for 80 percent NA. Similarly, `mice` speeds up from `r perc.hd.mi.div %>% max %>% round(., digits = 1)` to `r perc.hd.mi.div %>% min %>% round(., digits = 1)` times slower. 


```{r Runtimes Increased Missingness MAR Table, results='asis', echo=FALSE}

stargazer(run.all.perc, 
          summary = FALSE,
          align = TRUE,
          header = FALSE,
          rownames = FALSE,
          title = "Runtimes of Multiple Imputation Methods (in Minutes) by Percentage of Missingness (Framing Experiment Data)",
          label = "run.all.perc")

```






## Conclusion {#ordmiss-conclusion}

What doesn't work

-- Increasing percentage of NAs == worse `hd.ord` performance
-- Ordinal and interval variables == worse `hd.ord` performance
-- High number of observations == reduced number of iterations (crashes and/or RAM maxing out)
-- High number of observations == makes `amelia` faster relative to `hd.ord`
-- 17 ANES education levels == increases needed number of iterations
-- 17 ANES education levels == causes `amelia` to stop on CO and Jeff
-- 10,000 iterations == results with 1,000 iterations are just as good
-- `ampute` with `bycases=FALSE` and `cont=FALSE` == worse `hd.ord` performance, good `na.omit` performance
-- `own.NA` == `na.omit` performs best (currently in appendix)
-- `own.NA.rows`== pretty much everything is zero, incl. `na.omit`; `mice` is awful (currently in appendix)
-- Running `hd.ord` with `method = p.draw` == worse `hd.ord` performance
-- Running `hd.ord` with `method = p.draw` == only works with only binary vars in the data
-- Increasing `sdCutoff` == only does something with only binary vars in the data
-- Only binary vars in data == no gain in `hd.ord` performance

`own.NA` and `own.NA.rows` resulted in a strong performance of `na.omit`, which should not happen in a missingness mechanism that is supposed to be MAR. The functions thus likely represent a version of MCAR, which puts the usefulness of their imputation results in doubt.




What works

-- Results for binary variables == equal performance of `hd.ord`, `mice`, `amelia`
-- Increasing number of variables with NAs (all, not just binary) == better `hd.ord` performance
-- 1000 observations in data sets == increases `amelia` running time
-- MNAR == MAR in terms of `hd.ord` performance
-- Multiple ordinal variables == same performance as with one ordinal variable

